### 2019-07-30 PaperCVFAD2019/egpaper_final.tex
Add cvfad2019 paper

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcvfinal\pagestyle{empty}\fi

\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for ICCV Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
% Remove page # from the first page of camera-ready.
\ificcvfinal\thispagestyle{empty}\fi

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous ICCV abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Please follow the steps outlined below when submitting your manuscript to
the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against the
use of sticky tape to attach your artwork to the paper), so all authors
should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the ICCV 2019 web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section,
must be no longer than eight pages in length. The references section
will not be included in the page count, and there is no limit on the
length of the references section. For example, a paper of eight pages
with two pages of references would have a total length of 10 pages.

Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\iccvfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
tech reports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith; it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a tech report for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the tech report as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the ICCV70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.
\medskip

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper. For your results, however, you should not identify yourself and should not mention your participation in the challenge. Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.

Page numbers should be included for review submissions but not for the 
final paper. Review submissions papers should have page numbers in the 
footer with numbers centered and .75 inches (1.905 cm) from the bottom 
of the page and start on the first page with the number 1.

Page numbers will be added by the publisher to all camera-ready papers 
prior to including them in the proceedings and before submitting the 
papers to IEEE Xplore. As such, your camera-ready submission should 
not include any page numbers. Page numbers should automatically be 
removed by uncommenting (if it's not already) the line
\begin{verbatim}
% \iccvfinalcopy
\end{verbatim}
near the beginning of the .tex file.

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centered.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the ICCV 2019 web page for a discussion
of the use of color in your document.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2019-07-30 PaperCVFAD2019/egpaper_for_review.tex
Add cvfad2019 paper

--- 2019-07-30 PaperCVFAD2019/egpaper_final.tex
@@
 % run, let it finish, and you should be clear).
-\usepackage[breaklinks=true,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
-\iccvfinalcopy % *** Uncomment this line for the final submission
+% \iccvfinalcopy % *** Uncomment this line for the final submission
 
@@
 %%%%%%%%% TITLE
-\title{\LaTeX\ Author Guidelines for ICCV Proceedings}
+\title{CALVIS: Chest, wAist and peLVIS circumference from 3D human body meshes for deep learning}
 
@@
 
-Please follow the steps outlined below when submitting your manuscript to
-the IEEE Computer Society Press.  This style guide now has several
-important modifications (for example, you are no longer warned against the
-use of sticky tape to attach your artwork to the paper), so all authors
-should read this new version.
+We conduct two experiments.
+In the first experiment we synthesize 10 human body meshes.
+Then we apply our method to calculate chest, waist and pelvis circumference.
+We evaluate the results qualitatively.
+We observe that the measurements can indeed be used to estimate the shape of a person.
+The second experiment serves as a proof-of-concept where we input the calculated human dimensions to an artificial neural network.
+The idea is to establish the plausibility of our approach.
+After having trained the network with our data, we proof that the network is able to conduct this task.
 
-%-------------------------------------------------------------------------
-\subsection{Language}
-
-All manuscripts must be in English.
-
-\subsection{Dual submission}
-
-Please refer to the author guidelines on the ICCV 2019 web page for a
-discussion of the policy on dual submissions.
-
-\subsection{Paper length}
-Papers, excluding the references section,
-must be no longer than eight pages in length. The references section
-will not be included in the page count, and there is no limit on the
-length of the references section. For example, a paper of eight pages
-with two pages of references would have a total length of 10 pages.
-
-Overlength papers will simply not be reviewed.  This includes papers
-where the margins and formatting are deemed to have been significantly
-altered from those laid down by this style guide.  Note that this
-\LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for
-supervised revisions of manuscripts.  The reviewing process cannot determine
-the suitability of the paper for presentation in eight pages if it is
-reviewed in eleven.
-
-%-------------------------------------------------------------------------
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the
-version submitted for review.  The ruler is provided in order that
-reviewers may comment on particular lines in the paper without
-circumlocution.  If you are preparing a document using a non-\LaTeX\
-document preparation system, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the ruler
-should not change the appearance of any other content on the page.  The
-camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
-the \verb'\iccvfinalcopy' command in the document preamble.)  Reviewers:
-note that the ruler measurements do not align well with lines in the paper
---- this turns out to be very difficult to do well when the paper contains
-many figures and equations, and, when done, looks ugly.  Just use fractional
-references (e.g.\ this line is $095.5$), although in most cases one would
-expect that the approximate location will be adequate.
-
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations.  It is
-important for readers to be able to refer to any particular equation.  Just
-because you didn't refer to it in the text doesn't mean some future reader
-might not need to refer to it.  It is cumbersome to have to use
-circumlocutions like ``the equation second from the top of page 3 column
-1''.  (Note that the ruler will not be present in the final copy, so is not
-an alternative to equation numbers).  All authors will benefit from reading
-Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind
-review.  Blind review does not mean that one must remove
-citations to one's own work---in fact it is often impossible to
-review a paper unless the previous citations are known and
-available.
-
-Blind review means that you do not use the words ``my'' or ``our''
-when citing previous work.  That is all.  (But see below for
-tech reports.)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say
-that you are Lucy Smith; it says that you are building on her
-work.  If you are Smith and Jones, do not say ``as we show in
-[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
-paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our
-   previous paper [1], and show it to be inferior to all
-   previously known methods.  Why the previous paper was
-   accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the
-   paper of Smith \etal [1], and show it to be inferior to
-   all previously known methods.  Why the previous paper
-   was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo
-   filter, a fundamental contribution to human knowledge''.
-   Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time,
-which covers similar or overlapping material, you may need to refer to that
-submission in order to explain the differences, just as you would if you
-had previously published related work.  In such cases, include the
-anonymized parallel submission~\cite{Authors14} as additional material and
-cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
-Supplied as additional material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be
-found elsewhere, and refer them to a technical report.  For conference
-submissions, the paper must stand on its own, and not {\em require} the
-reviewer to go to a tech report for further details.  Thus, you may say in
-the body of the paper ``further details may be found
-in~\cite{Authors14b}''.  Then submit the tech report as additional material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool which
-is widely known to be restricted to a single institution.  For example,
-let's say it's 1969, you have solved a key problem on the Apollo lander,
-and you believe that the ICCV70 audience would like to hear about your
-solution.  The work is a development of your celebrated 1968 paper entitled
-``Zero-g frobnication: How being the only people in the world with access to
-the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.  Don't write ``We show how to
-improve our previous work [Anonymous, 1968].  This time we tested the
-algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors. Instead
-write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.  This
-   system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] didn't
-   handle case B properly.  Ours handles it by including
-   a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo
-   lunar lander, and went all the way to the moon, don't
-   you know.  It displayed the following behaviours
-   which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention,
-reads better than the first version, and does not explicitly name you as
-the authors.  A reviewer might think it likely that the new paper was
-written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been
-contracted to solve problem B.
-\medskip
-
-\noindent
-FAQ\medskip\\
-{\bf Q:} Are acknowledgements OK?\\
-{\bf A:} No.  Leave them for the final copy.\medskip\\
-{\bf Q:} How do I cite my results reported in open challenges?
-{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-
-\begin{figure}[t]
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
-
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a
-sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
-\verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'',
-shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
-However, use it only when there are three or more authors.  Thus, the
-following is correct: ``
-   Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
-because reference~\cite{Alpher03} has just two authors.  If you use the
-\verb'\etal' macro provided, then you need not worry about double periods
-when used at the end of a sentence as in Alpher \etal.
-
-For this citation style, keep multiple citations in numerical (not
-chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-\cite{Alpher02,Alpher03,Authors14}.
-
-\begin{figure*}
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-\end{center}
-   \caption{Example of a short caption, which should be centered.}
-\label{fig:short}
-\end{figure*}
+Problem statement: given a 3D human body mesh $\mathcal{M}$ we look for a method able to automatically output chest, waist and pelvis circumference.
 
 %------------------------------------------------------------------------
-\section{Formatting your paper}
-
-All text must be in a two-column format. The total allowable width of the
-text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
-cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
-$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
-first page) should begin 1.0 inch (2.54 cm) from the top edge of the
-page. The second and following pages should begin 1.0 inch (2.54 cm) from
-the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
-cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
-paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
-page.
-
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-high.
-
-Page numbers should be included for review submissions but not for the 
-final paper. Review submissions papers should have page numbers in the 
-footer with numbers centered and .75 inches (1.905 cm) from the bottom 
-of the page and start on the first page with the number 1.
-
-Page numbers will be added by the publisher to all camera-ready papers 
-prior to including them in the proceedings and before submitting the 
-papers to IEEE Xplore. As such, your camera-ready submission should 
-not include any page numbers. Page numbers should automatically be 
-removed by uncommenting (if it's not already) the line
-\begin{verbatim}
-% \iccvfinalcopy
-\end{verbatim}
-near the beginning of the .tex file.
-
-%-------------------------------------------------------------------------
-\subsection{Type-style and fonts}
-
-Wherever Times is specified, Times Roman may also be used. If neither is
-available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
-the first page. The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
-adverbs; do not capitalize articles, coordinate conjunctions, or
-prepositions (unless the title begins with such a word). Leave two blank
-lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type. This information is to
-be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
-double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
-inch or 0.422 cm). Make sure your text is fully justified---that is,
-flush left and flush right. Please do not place any additional blank
-lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in
-Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centered.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-,
-second-, and third-order headings.
-
-FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
-should be Times 12-point boldface, initially capitalized, flush left,
-with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
-should be Times 11-point boldface, initially capitalized, flush left,
-with one blank line before, and one after. If you require a third-order
-heading (we discourage it), use 10-point Times, boldface, initially
-capitalized, flush left, preceded by one blank line, followed by a period
-and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote {This is what a footnote looks like.  It
-often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral
-observations in
-the text (within parentheses, if you prefer, as in this sentence).  If you
-wish to use a footnote, place it at the bottom of the column on the page on
-which it is referenced. Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times,
-single-spaced, at the end of your paper. When referenced in the text,
-enclose the citation number in square brackets, for
-example~\cite{Authors14}.  Where appropriate, include the name(s) of
-editors of referenced books.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|c|}
-\hline
-Method & Frobnability \\
-\hline\hline
-Theirs & Frumpy \\
-Yours & Frobbly \\
-Ours & Makes one's heart Frob\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Results.   Ours is better.}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.  Please ensure that any point you wish to
-make is resolvable in a printed copy of the paper.  Resize fonts in figures
-to match the font in the body text, and choose line widths which render
-effectively in print.  Many readers (and reviewers), even of an electronic
-copy, will choose to print your paper in order to read it.  You cannot
-insist that they do otherwise, and therefore must not assume that they can
-zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use
-\verb+\includegraphics+, and to specify the  figure width as a multiple of
-the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the ICCV 2019 web page for a discussion
-of the use of color in your document.
+\section{Approach}
+We asume that the body mesh has RTP orientation.
+If the mesh has another orientation we can always rotate and translate the mesh to brig it to RTP orientation.
+Next, we slice the mesh with a 0,1mm.
+The planes intersecting the body contain countour.
+We use the library trimesh to calculate the length of the perimeter.
 
 %------------------------------------------------------------------------
-\section{Final copy}
+\section{Experiments and Results}
+
+%------------------------------------------------------------------------
+\section{Conclusion}
 

### 2019-07-30 PaperCVFAD2019/egpaper_for_review.tex
describe approach

@@
 %%%%%%%%% TITLE
-\title{CALVIS: Chest, wAist and peLVIS circumference from 3D human body meshes for deep learning}
+\title{CALVIS: Chest, wAist and peLVIS circumference from 3D human body meshes 
+as ground truth for deep learning}
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
+\author{Yansel González Tejeda\\
+Paris Lodron University of Salzburg\\
+{\tt\small yansel.gonzalez-tejeda@stud.sbg.ac.at}
 % For a paper whose authors are all at the same institution,
@@
 \and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+Helmut Mayer\\
+{\tt\small helmut@cosy.sbg.ac.at}
 }
@@
 \begin{abstract}
-   The ABSTRACT is to be in fully-justified italicized text, at the top
-   of the left-hand column, below the author and affiliation
-   information. Use the word ``Abstract'' as the title, in 12-point
-   Times, boldface type, centered relative to the column, initially
-   capitalized. The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous ICCV abstracts to get a feel for style and length.
+   In this paper we present CALVIS, a method to calculate chest, waist and 
+   pelvis circumference from 3D human body meshes. The idea is to use these 
+   human body dimensions as ground truth for deep learning. Previous work had 
+   used the large scale CAESAR dataset, calculated $\textit{manually}$ these 
+   anthropometrical measurements or directly acquired them from a person. The 
+   problem is that acquiring these data is a cost and time consuming endeavor. 
+   Hence, instead of measuring real people, we employ a generative model of 
+   humans, which is able to generate any number of humans with different shapes 
+   and poses from a single human template. We then compute chest, waist and 
+   pelvis circumference from these models (represented as a 3D mesh) to 
+   balabla. We conduct two experiments. In the first experiment we synthesize 
+   10 human body meshes. Then we apply CALVIS to calculate chest, waist and 
+   pelvis circumference. We evaluate the results qualitatively. We observe that 
+   the measurements can indeed be used to estimate the shape of a person. The 
+   second experiment serves as a proof-of-concept where we use the calculated 
+   human dimensions as a ground truth to train an artificial neural network. 
+   The idea is to establish the plausibility of our approach. After having 
+   trained the network with our 
+   data, we proof that the network is able to conduct this task.
 \end{abstract}
@@
 \section{Introduction}
+
+The general idea is to train a prediction model (in our case a {\em 
+convolutional neural network} (CNN)) with examples of images of humans whose 
+body measurements are known, and use the trained model as a predictor of body 
+dimensions given arbitrary images of humans. The main problem with this 
+approach is a sufficient number of available training data, as acquiring these 
+data is a cost and time consuming endeavor. Hence, instead of measuring real 
+people, we employ a generative model of humans, which is able to generate any 
+number of humans with different shapes and poses from a single human template. 
+We then compute the body dimensions algorithmically from these models 
+(represented as a 3D mesh) to be used as ground truth for synthetic images of 
+the model.
 
@@
 
-Problem statement: given a 3D human body mesh $\mathcal{M}$ we look for a method able to automatically output chest, waist and pelvis circumference.
+Problem statement: given a 3D human body mesh $\mathcal{M}$ we look for a 
+method capable to automatically output chest, waist and pelvis circumference.
 
@@
 \section{Approach}
-We asume that the body mesh has RTP orientation.
-If the mesh has another orientation we can always rotate and translate the mesh to brig it to RTP orientation.
-Next, we slice the mesh with a 0,1mm.
-The planes intersecting the body contain countour.
-We use the library trimesh to calculate the length of the perimeter.
+In this work we synthesize 3D human meshes using the SMPL
+model \cite{Loper.2015}. This model is at its top level a skinned articulated 
+model, i.e., 
+consists of a 
+surface mesh that mimics the skin and a skeleton related to that mesh. It is 
+defined by a mean 
+template shape represented by a vector of $N$ concatenated vertices 
+$\mathbf{\bar{T}}$ in the zero pose, $\vec{\theta}$. In order to synthesize a 
+new human mesh one has to deform the provided template mesh by 
+setting shape parameters $\vec{\beta}$ and pose parameters $\vec{\theta}$. The 
+model provides learned parameters
+\begin{equation} \label{eq:smpl_params}
+\Phi = \{\mathbf{\bar{T}}, \mathcal{W}, \mathcal{S}, \mathcal{J}, 
+\mathcal{P}\}
+\end{equation}
+As mentioned above $\mathbf{\bar{T}}$ is the mean template shape. The weight 
+matrix $\mathcal{W}$ represents how much the rotation of skeleton parts affects 
+the vertices. In addition, the matrices $\mathcal{S}$ and $\mathcal{P}$ define 
+linear functions that are used to deform $\mathbf{\bar{T}}$ and the matrix 
+$\mathcal{J}$ predicts skeleton rest joint locations from vertices in the rest 
+pose. We held fix these parameters during the synthesis.
+
+Let us consider a human body mesh $\mathcal{M}$. Our method requires that 
+$\mathcal{M}$ is standing with arms raised 
+parallel to the 
+ground at shoulder height at a $90^\circ$ angle. In the line 
+of previous work (\cite{Dibra.2016a})), we name this pose the zero (also 
+normalized (rf)) pose $\vec{\theta}^*$. Additionally, we assume that the mesh 
+has LSA orientation, e.g., x, y and z axis are positively directed from 
+right-to-left, inferior-to-superior and posterior-to-anterior, respectively. If 
+the mesh has another orientation we can always apply transformations to orient 
+it LSA.
+
+Intuitively, we would like to measure the chest circumference bellow the arms 
+at the widest part of the torso and the waist circumference at the 
+narrowest part after the chest but above the hips. Similarly, the hip 
+circumference is measured often around the widest part of hips and buttocks. We 
+can formalize this intuition by considering the cross-sectional length of the 
+2D curve along the y-axis. Since $\mathcal{M}$ is triangulated, we can use a 
+plane $\boldsymbol{\pi}$ to intersect the mesh. The boundary of this 
+intersection is a collection of connected segments $s_i$. Therefore, we can 
+determine this boundary length as
+\begin{align}
+BL = \sum_{i = 1}^{i = n}s_i
+\end{align}
+
+Next, starting from the bounding box top part we cut the mesh into evenly 
+spaced slices $m$ and compute the total sum.
 

### 2019-08-01 PaperCVFAD2019/egpaper_for_review.tex
mesh signature

@@
    In this paper we present CALVIS, a method to calculate chest, waist and 
-   pelvis circumference from 3D human body meshes. The idea is to use these 
-   human body dimensions as ground truth for deep learning. Previous work had 
-   used the large scale CAESAR dataset, calculated $\textit{manually}$ these 
-   anthropometrical measurements or directly acquired them from a person. The 
-   problem is that acquiring these data is a cost and time consuming endeavor. 
-   Hence, instead of measuring real people, we employ a generative model of 
-   humans, which is able to generate any number of humans with different shapes 
-   and poses from a single human template. We then compute chest, waist and 
-   pelvis circumference from these models (represented as a 3D mesh) to 
-   balabla. We conduct two experiments. In the first experiment we synthesize 
-   10 human body meshes. Then we apply CALVIS to calculate chest, waist and 
-   pelvis circumference. We evaluate the results qualitatively. We observe that 
-   the measurements can indeed be used to estimate the shape of a person. The 
-   second experiment serves as a proof-of-concept where we use the calculated 
-   human dimensions as a ground truth to train an artificial neural network. 
-   The idea is to establish the plausibility of our approach. After having 
-   trained the network with our 
-   data, we proof that the network is able to conduct this task.
+   pelvis circumference from 3D human body meshes. Our motivation is to use 
+   this data as ground truth for learning with convolutional neural networks 
+   (CNN). Previous work had used the large scale CAESAR dataset, determined 
+   $\textit{manually}$ these anthropometrical measurements or directly acquired 
+   them from a person. The problem is that acquiring these data is a cost and 
+   time consuming endeavor. In contrast our method can be used on 
+   3D meshes automatically. First, we slice cross sections along the Y axis of 
+   the mesh. Second, we calculate the cross sections length and establish a 
+   signature for the body represented by the mesh. Finally, using this 
+   signature we are able to calculate the chest, waist and pelvis 
+   circumference by searching for critical points. We conduct two experiments. 
+   In the first experiment we synthesize 10 human body meshes. Then we apply 
+   CALVIS to calculate chest, waist and pelvis circumference. We evaluate the 
+   results qualitatively. We observe that the measurements can indeed be used 
+   to estimate the shape of a person. The second experiment serves as a 
+   proof-of-concept where we use the calculated human dimensions as a ground 
+   truth to train a small CNN. The idea is to establish the plausibility of our 
+   approach. After having trained the network with our data, we demonstrate 
+   that learning converges, achieving a 3 percent prediction error. 
+   Furthermore, we make the implementation of CALVIS publicly available to 
+   advance the field.
 \end{abstract}
@@
 
-The general idea is to train a prediction model (in our case a {\em 
-convolutional neural network} (CNN)) with examples of images of humans whose 
-body measurements are known, and use the trained model as a predictor of body 
-dimensions given arbitrary images of humans. The main problem with this 
-approach is a sufficient number of available training data, as acquiring these 
-data is a cost and time consuming endeavor. Hence, instead of measuring real 
-people, we employ a generative model of humans, which is able to generate any 
-number of humans with different shapes and poses from a single human template. 
-We then compute the body dimensions algorithmically from these models 
-(represented as a 3D mesh) to be used as ground truth for synthetic images of 
-the model.
+\textbf{Motivation} 
+Predicting 3D human body measurements from images is crucial in several 
+scenarios 
+like virtual try-on, animating, ergonomics, computational forensics and 
+even health and mortality estimation. Researches had 
+named this 
+measurements body intuitive controls (\cite{Allen.2003}), biometric 
+measurements (\cite{Sigal.2008}), body dimensions 
+(\cite{DBLP:conf/bmvc/ChenRC11}), semantical parameters (\cite{Yang.2014}), 
+traditional anthropometric 
+measurements 
+(\cite{Wuhrer2011}) or only ``shape" as in human shape estimation 
+(\cite{Guan.2013}, \cite{Bogo:ECCV:2016}, \cite{Loper.2015}, 
+\cite{Dibra.2016a}, \cite{Pishchulin.2017}). In contrast, we assume a more 
+anthropometric approach 
+motivated by comprehensive compendiums like Panero and Zelnik, 1979 
+\cite{panero1979human}.
+Throughout this paper the term human body 
+dimensions 
+will be used to refer to the above measurements.
 
-We conduct two experiments.
-In the first experiment we synthesize 10 human body meshes.
-Then we apply our method to calculate chest, waist and pelvis circumference.
-We evaluate the results qualitatively.
-We observe that the measurements can indeed be used to estimate the shape of a person.
-The second experiment serves as a proof-of-concept where we input the calculated human dimensions to an artificial neural network.
-The idea is to establish the plausibility of our approach.
-After having trained the network with our data, we proof that the network is able to conduct this task.
+The problem of estimating human body dimensions  
+having only an image is an under-constrained  (or inverse) problem. Information 
+gets lost when a camera is 
+used to capture the human body in 3D space to 'render' a 2D image.
+
+To tackle this problem a supervised learning approach can be used. This approach
+demands large amount of human body anthropometric measurements and is certainly 
+one of the biggest challenges in the field.  Currently there 
+is only one large-scale dataset, the Civilian American and 
+European Surface Anthropometry Resource (CAESAR) \cite{robinette1999caesar} 
+with 3D human body scans and their corresponding anthropometric measurements. 
+This survey was extraordinarily large and resource intensive: around nine 
+thousand people from Europe and the USA where scanned, it was conducted over 
+more than five years and costed more than six million dollars.
+
+In the past decade a noticeably amount of researchers have employed this 
+dataset to investigate human shape estimation. Because the measurement 
+acquiring process is resource intensive and requires large amount of human and 
+material resources, this type of studies are rare and the data they offer is 
+expensive. Therefore, it is important to explore alternative methods where 
+human body measurements derived from real data can be obtained for 
+investigation.
+
+3D human body generative models offers such an alternative. We propose to 
+synthesize 3D human body meshes using the SMPL \cite{Loper.2015} generative 
+model. Once we have 
+the 3D meshes we can compute chest, waist and pelvis circumference. The next 
+step after obtaining the 
+measurements is to use a camera model to render
+images. Finally, in possession of this ground truth we can 
+input this images to the learning algorithm and perform inference.
+
+Explain method here in a very succinct way. balslfas iourgioafdnsva 
+ihasoifghksv kiashdikhjioapgjgf oiasjojaspofdgjaposjg aisfhdgipoashfgihasghj 
+aishgfiashgiahsfighaishg ihaspioghpaioshgpiasfgpi 
+pjasoip09erujfdnaihg8qzßehgiqhfe.
 
@@
 \section{Approach}
+
 In this work we synthesize 3D human meshes using the SMPL
@@
 template shape represented by a vector of $N$ concatenated vertices 
-$\mathbf{\bar{T}}$ in the zero pose, $\vec{\theta}$. In order to synthesize a 
+$\mathbf{\bar{T}}$ in the zero pose, $\vec{\theta}^*$. In order 
+to 
+synthesize a 
 new human mesh one has to deform the provided template mesh by 
@@
 
+\subsection{Human Body Mesh Signature}
 Let us consider a human body mesh $\mathcal{M}$. Our method requires that 
@@
 ground at shoulder height at a $90^\circ$ angle. In the line 
-of previous work (\cite{Dibra.2016a})), we name this pose the zero (also 
+of previous work (\cite{Dibra.2016a}), we name this pose the zero (also 
 normalized (rf)) pose $\vec{\theta}^*$. Additionally, we assume that the mesh 
@@
 right-to-left, inferior-to-superior and posterior-to-anterior, respectively. If 
-the mesh has another orientation we can always apply transformations to orient 
-it LSA.
+the mesh has another orientation we can always apply transformations to 
+LSA-align it.
 
@@
 can formalize this intuition by considering the cross-sectional length of the 
-2D curve along the y-axis. Since $\mathcal{M}$ is triangulated, we can use a 
-plane $\boldsymbol{\pi}$ to intersect the mesh. The boundary of this 
-intersection is a collection of connected segments $s_i$. Therefore, we can 
-determine this boundary length as
+2D intersection curves (\cite{book.compu.topo}) along the y-axis. Moreover, we 
+can 
+use a plane $\boldsymbol{\pi}$ parallel to the floor to intersect the mesh. 
+Since $\mathcal{M}$ is 
+triangulated, the boundary of this 
+intersection is a collection of segments $s_i$. Therefore, we can 
+determine the boundary length as at point j
 \begin{align}
-BL = \sum_{i = 1}^{i = n}s_i
+\mathcal{BL}_j = \sum_{i = 1}^{i = n}s_i
 \end{align}
 
-Next, starting from the bounding box top part we cut the mesh into evenly 
-spaced slices $m$ and compute the total sum.
+Note that for cross sections where $\boldsymbol{\pi}$ intersects the legs two 
+disconnected curves will appear. That is by no means a problem because they are 
+still a collection of segment with non-zero length.
+
+\begin{figure}[t]
+	\begin{center}
+		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+		\includegraphics[width=\linewidth]{Figure_1.eps}
+	\end{center}
+	\caption{Human Body Mesh Signature for male and female meshes}
+	\label{fig:hbm_signature}
+\end{figure}
+
+Next, starting from the top of the bounding box we cut the mesh into evenly 
+spaced slices $m$. For every slice j, we compute $BL_j$. Finally, we can 
+construct the human body \textbf{mesh signature} $\mathcal{MS}$ of mesh 
+$\mathcal{M}$ in the zero pose $\vec{\theta}^*$
+
+\begin{align}
+\mathcal{MS}(\mathcal{M}, \vec{\theta}^*, j) = \mathcal{BL}_j, \, j \in \{1, 
+\cdots, m\}
+\end{align}
+
+Figure \ref{fig:hbm_signature} shows the $\mathcal{MS}$ for two meshes. The 
+function resembles a rotated silhouette of the human body and exhibits a number 
+of critical points.
+
+\subsection{Critical Points on Mesh Signature}
 
@@
 \section{Experiments and Results}
+
+We conduct two experiments. In the first experiment we synthesize 10 human body 
+meshes. Then we apply our method to calculate chest, waist and pelvis 
+circumference. We evaluate the results qualitatively. We observe that the 
+measurements can indeed be used to estimate the shape of a person. The second 
+experiment serves as a proof-of-concept where we input the calculated human 
+dimensions to an artificial neural network. The idea is to establish the 
+plausibility of our approach. After having trained the network with our data, 
+we proof that the network is able to conduct this task.
 

### 2019-08-02 PaperCVFAD2019/egpaper_for_review.tex
mesh signature extrema

@@
 intersection is a collection of segments $s_i$. Therefore, we can 
-determine the boundary length as at point j
+determine the boundary length by specifying a point along the y-axis $j$ as
 \begin{align}
-\mathcal{BL}_j = \sum_{i = 1}^{i = n}s_i
+\mathcal{BL}(\mathcal{M}, \boldsymbol{\pi}, j) = \sum_{i = 
+1}^{i = n}s_i
 \end{align}
 
-Note that for cross sections where $\boldsymbol{\pi}$ intersects the legs two 
+Note that for cross sections where $\boldsymbol{\pi}$ intersects the legs, two 
 disconnected curves will appear. That is by no means a problem because they are 
@@
 	\end{center}
-	\caption{Human Body Mesh Signature for male and female meshes}
+	\caption{Human Body Mesh Signature for male and female meshes. The 
+		function resembles a rotated silhouette of the human body and exhibits 
+		several \textit{extrema}.}
 	\label{fig:hbm_signature}
@@
 
-Next, starting from the top of the bounding box we cut the mesh into evenly 
-spaced slices $m$. For every slice j, we compute $BL_j$. Finally, we can 
-construct the human body \textbf{mesh signature} $\mathcal{MS}$ of mesh 
-$\mathcal{M}$ in the zero pose $\vec{\theta}^*$
+Next, we assemble the mesh slide length vector $\vec{\mathcal{L}}$. Starting 
+from the 
+top $j_t$ of the bounding box we cut the mesh into 
+evenly 
+$m$-meters spaced slices until we reach the bounding box bottom $j_b$. For 
+every 
+slice at point $j$, we compute $\mathcal{BL}(j)$.
 
 \begin{align}
-\mathcal{MS}(\mathcal{M}, \vec{\theta}^*, j) = \mathcal{BL}_j, \, j \in \{1, 
-\cdots, m\}
+\vec{\mathcal{L}} = \mathcal{BL}(j), \, j 
+\in 
+\{j_t, j_t+m, \cdots, j_b\}
 \end{align}
 
-Figure \ref{fig:hbm_signature} shows the $\mathcal{MS}$ for two meshes. The 
-function resembles a rotated silhouette of the human body and exhibits a number 
-of critical points.
+Finally, we can construct the human body \textbf{mesh signature} $\mathcal{MS}: 
+\mathbb{Z}^+ \to \mathbb{R}$ of mesh $\mathcal{M}$ sliced iterative by plane 
+$\boldsymbol{\pi}$ every $m$-meters by setting its value to the value of 
+$\vec{\mathcal{L}}$ at 
+slide index $x$
 
-\subsection{Critical Points on Mesh Signature}
+\begin{align}\label{eq:mesh_signature}
+\mathcal{MS}(\mathcal{M}, \boldsymbol{\pi}, m) = \vec{\mathcal{L}}(x), \, x \in 
+\{0, 1, \cdots\}
+\end{align}
+
+Figure \ref{fig:hbm_signature} shows the $\mathcal{MS}$ of two meshes (male 
+and female) for 
+$m=0,001$ and plane $\boldsymbol{\pi}$ parallel to the floor (with normal $(0, 
+1,0)$) using the library trimesh \cite{trimesh}. The 
+function resembles a rotated silhouette of the human body and exhibits several 
+\textit{extrema}.
+
+\subsection{Mesh Signature Extrema}
+
+By comparing neighboring values of the mesh signature $\mathcal{MS}$ as defined 
+in equation \ref{eq:mesh_signature} we find several \textit{extrema}. In 
+general, we use these \textit{extrema} as features to 
+calculate the human dimensions. More specifically, we assume that:
+\begin{enumerate}
+	\item The global maximum $M_g$ represents the length of the largest path 
+	around the arms.
+	\item The local maximum $M_{hc}$ with largest value other than $M_g$ 
+	immediately posterior to it represents the hip circumference.
+	\item The local minimum $M_{wc}$ posterior to $M_g$ but prior to $M_{hc}$ 
+	represents hip circumference.
+	\item The local maximum $M_{cc}$ posterior to $M_g$ but prior to $M_{wc}$ 
+	represents chest circumference.
+\end{enumerate}
 

### 2019-08-06 PaperCVFAD2019/egpaper_for_review.tex
add extrema

@@
 intersection is a collection of segments $s_i$. Therefore, we can 
-determine the boundary length by specifying a point along the y-axis $j$ as
+determine the boundary length by specifying a point along the y-axis $j \in 
+\mathbb{R}$ as
 \begin{align}
@@
 from the 
-top $j_t$ of the bounding box we cut the mesh into 
-evenly 
-$m$-meters spaced slices until we reach the bounding box bottom $j_b$. For 
-every 
-slice at point $j$, we compute $\mathcal{BL}(j)$.
+top $j_t$ of the bounding box we sliced iterative mesh $\mathcal{M}$ with plane 
+$\boldsymbol{\pi}$ every $m$-meters until we reach the bounding box bottom 
+$j_b$. For every slice at point $j$, we compute $\mathcal{BL}(j)$.
 
 \begin{align}
-\vec{\mathcal{L}} = \mathcal{BL}(j), \, j 
+\vec{\mathcal{L}}(\mathcal{M}, \boldsymbol{\pi}, m) = \mathcal{BL}(j), \, j 
 \in 
@@
 Finally, we can construct the human body \textbf{mesh signature} $\mathcal{MS}: 
-\mathbb{Z}^+ \to \mathbb{R}$ of mesh $\mathcal{M}$ sliced iterative by plane 
-$\boldsymbol{\pi}$ every $m$-meters by setting its value to the value of 
-$\vec{\mathcal{L}}$ at 
-slide index $x$
+\mathbb{Z}^+ \to \mathbb{R}$ that maps every slice index $k \in \{0, 1, \cdots, 
+|\mathcal{L}|-1\}$ to the corresponding boundary length $\mathcal{BL}(j)$ in 
+the mesh slide vector $\vec{\mathcal{L}}$.
 
 \begin{align}\label{eq:mesh_signature}
-\mathcal{MS}(\mathcal{M}, \boldsymbol{\pi}, m) = \vec{\mathcal{L}}(x), \, x \in 
-\{0, 1, \cdots\}
+\mathcal{MS}(k) = \mathcal{BL}(j)
 \end{align}
@@
 $m=0,001$ and plane $\boldsymbol{\pi}$ parallel to the floor (with normal $(0, 
-1,0)$) using the library trimesh \cite{trimesh}. The 
-function resembles a rotated silhouette of the human body and exhibits several 
+1,0)$) using the library trimesh \cite{trimesh}. Note that the function as 
+defined by equation \ref{eq:mesh_signature} is bounded and not continuous. It 
+resembles a rotated silhouette of the human body and exhibits several 
 \textit{extrema}.
@@
 in equation \ref{eq:mesh_signature} we find several \textit{extrema}. In 
-general, we use these \textit{extrema} as features to 
+general, we expect these \textit{extrema} to be adequate features to 
 calculate the human dimensions. More specifically, we assume that:
@@
 	\item The global maximum $M_g$ represents the length of the largest path 
-	around the arms.
+	around the arms. From a topographic point of view $M_g$ is the highest peak 
+	of $\mathcal{MS}$.   
 	\item The local maximum $M_{hc}$ with largest value other than $M_g$ 
@@
 	\item The local minimum $M_{wc}$ posterior to $M_g$ but prior to $M_{hc}$ 
-	represents hip circumference.
-	\item The local maximum $M_{cc}$ posterior to $M_g$ but prior to $M_{wc}$ 
-	represents chest circumference.
+	represents waist circumference.
+	\item from a topograhpic point of view $M_g$ is a peak from  	
+	The local maximum $M_{cc}$ posterior to $M_g$ but prior to $M_{wc}$ 
+	represents 
+	chest circumference. If this local maximum does not exist we set $M_{cc}$ 
+	to the value of the path $\mathcal{BL}(j_{cc})$ with largest value $M_{cc}$ 
+	posterior 
+	to 
+	$M_g$ and difference at least $\delta$ to it but prior to $M_{wc}$	
+	represents 
+	chest circumference.
 \end{enumerate}
@@
 We conduct two experiments. In the first experiment we synthesize 10 human body 
-meshes. Then we apply our method to calculate chest, waist and pelvis 
-circumference. We evaluate the results qualitatively. We observe that the 
+meshes. Then we apply CALVIS to calculate chest, waist and pelvis 
+circumference. We evaluate the results qualitatively by comparing our method 
+with \cite{Dibra.2016b}. We observe that the 
 measurements can indeed be used to estimate the shape of a person. The second 

### 2019-08-30 PaperCVFAD2019/egpaper_for_review.tex
add rmfi paper

@@
 
-% \iccvfinalcopy % *** Uncomment this line for the final submission
+ \iccvfinalcopy % *** Uncomment this line for the final submission
 
@@
 Helmut Mayer\\
+Paris Lodron University of Salzburg\\
 {\tt\small helmut@cosy.sbg.ac.at}
@@
    signature we are able to calculate the chest, waist and pelvis 
-   circumference by searching for critical points. We conduct two experiments. 
+   circumference by searching for extrema. We conduct two experiments. 
    In the first experiment we synthesize 10 human body meshes. Then we apply 
@@
    results qualitatively. We observe that the measurements can indeed be used 
-   to estimate the shape of a person. The second experiment serves as a 
-   proof-of-concept where we use the calculated human dimensions as a ground 
-   truth to train a small CNN. The idea is to establish the plausibility of our 
-   approach. After having trained the network with our data, we demonstrate 
-   that learning converges, achieving a 3 percent prediction error. 
+   to estimate the shape of a person. The second experiment asses the 
+   plausibility of our approach where we use the calculated human dimensions as 
+   a ground truth to train a small CNN. After having trained the network with 
+   our data, we demonstrate that learning converges, achieving $x$ percent 
+   prediction error. 
    Furthermore, we make the implementation of CALVIS publicly available to 
@@
 
-Explain method here in a very succinct way. balslfas iourgioafdnsva 
-ihasoifghksv kiashdikhjioapgjgf oiasjojaspofdgjaposjg aisfhdgipoashfgihasghj 
-aishgfiashgiahsfighaishg ihaspioghpaioshgpiasfgpi 
-pjasoip09erujfdnaihg8qzßehgiqhfe.
-
 Problem statement: given a 3D human body mesh $\mathcal{M}$ we look for a 
@@
 %------------------------------------------------------------------------
-\section{Approach}
+\section{Approach}\label{sec:approach}
 
@@
 
-\subsection{Human Body Mesh Signature}
+\subsection{Human Body Mesh Signature}\label{subsec:hbm_signature}
 Let us consider a human body mesh $\mathcal{M}$. Our method requires that 
@@
 at the widest part of the torso and the waist circumference at the 
-narrowest part after the chest but above the hips. Similarly, the hip 
+narrowest part after the chest but above the hips. Similarly, the pelvis 
 circumference is measured often around the widest part of hips and buttocks. We 
@@
 		function resembles a rotated silhouette of the human body and exhibits 
-		several \textit{extrema}.}
+		several \textit{extrema}. See section 
+		\ref{subsec:mesh_signature_extrema} for discussion of these extrema.}
 	\label{fig:hbm_signature}
@@
 
-\subsection{Mesh Signature Extrema}
+\subsection{Mesh Signature Extrema}\label{subsec:mesh_signature_extrema}
 
@@
 	around the arms. From a topographic point of view $M_g$ is the highest peak 
-	of $\mathcal{MS}$.   
-	\item The local maximum $M_{hc}$ with largest value other than $M_g$ 
-	immediately posterior to it represents the hip circumference.
-	\item The local minimum $M_{wc}$ posterior to $M_g$ but prior to $M_{hc}$ 
+	of $\mathcal{MS}$. A horizontal line at height proportion $h$ of the peak 
+	intersects 
+	it at two points left $p_l$ and right $p_r$.
+	\item The local maximum $M_{pc}$ with largest value other than $M_g$ 
+	immediately posterior to $p_r$ represents the pelvis circumference.
+	\item The local minimum $M_{wc}$ posterior to $p_r$ but prior to $M_{pc}$ 
 	represents waist circumference.
-	\item from a topograhpic point of view $M_g$ is a peak from  	
-	The local maximum $M_{cc}$ posterior to $M_g$ but prior to $M_{wc}$ 
+	\item The local maximum $M_{cc}$ posterior to $p_r$ but prior to $M_{wc}$ 
 	represents 
 	chest circumference. If this local maximum does not exist we set $M_{cc}$ 
-	to the value of the path $\mathcal{BL}(j_{cc})$ with largest value $M_{cc}$ 
-	posterior 
-	to 
-	$M_g$ and difference at least $\delta$ to it but prior to $M_{wc}$	
-	represents 
-	chest circumference.
+	to the value of the path $\mathcal{BL}(j_{cc})$ with largest value in the 
+	interval $(p_l; M_{wc})$.
 \end{enumerate}
@@
 
-We conduct two experiments. In the first experiment we synthesize 10 human body 
-meshes. Then we apply CALVIS to calculate chest, waist and pelvis 
-circumference. We evaluate the results qualitatively by comparing our method 
-with \cite{Dibra.2016b}. We observe that the 
-measurements can indeed be used to estimate the shape of a person. The second 
-experiment serves as a proof-of-concept where we input the calculated human 
-dimensions to an artificial neural network. The idea is to establish the 
-plausibility of our approach. After having trained the network with our data, 
-we proof that the network is able to conduct this task.
+We conduct two experiments. In the first experiment we synthesize eight (four 
+female and four male) human body meshes using shape parameters provided by 
+SURREAL \cite{varol17_surreal}.
+The meshes reflect human figures characteristics such as bulky, slim, small and 
+tall subjects. Then we apply CALVIS to calculate chest, waist and pelvis 
+circumference. Since we do not have ground truth, we evaluate the results 
+qualitatively by comparing our method 
+with \cite{Dibra.2016b}.
+The second 
+experiment serves to asses the plausibility of our approach to use the 
+synthetic data for deep learning. We input the calculated human 
+dimensions to an artificial neural network. After having trained the network 
+with our data, we show that learning converges.
 
@@
 
-You must include your signed IEEE copyright release form when you submit
-your finished paper. We MUST have this form before your paper can be
-published in the proceedings.
+The method can be optimized. Further research must be conducted.
 

### 2019-08-30 PaperRMFI2019/samplepaper.tex
add rmfi paper

--- 2019-08-30 PaperCVFAD2019/egpaper_for_review.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{iccv}
-\usepackage{times}
-\usepackage{epsfig}
+% This is samplepaper.tex, a sample chapter demonstrating the
+% LLNCS macro package for Springer Computer Science proceedings;
+% Version 2.20 of 2017/10/04
+%
+\documentclass[runningheads]{llncs}
+%
 \usepackage{graphicx}
+% Used for displaying a sample figure. If possible, figure files should
+% be included in EPS format.
 \usepackage{amsmath}
 \usepackage{amssymb}
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
+%
+% If you use the hyperref package, please uncomment the following line
+% to display URLs in blue roman font according to Springer's eBook style:
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
- \iccvfinalcopy % *** Uncomment this line for the final submission
-
-\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ificcvfinal\pagestyle{empty}\fi
+\renewcommand\UrlFont{\color{blue}\rmfamily}
 
 \begin{document}
-
-%%%%%%%%% TITLE
+%
 \title{CALVIS: Chest, wAist and peLVIS circumference from 3D human body meshes	
 as ground truth for deep learning}
-
-\author{Yansel González Tejeda\\
-Paris Lodron University of Salzburg\\
-{\tt\small yansel.gonzalez-tejeda@stud.sbg.ac.at}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Helmut Mayer\\
-Paris Lodron University of Salzburg\\
-{\tt\small helmut@cosy.sbg.ac.at}
-}
-
-\maketitle
-% Remove page # from the first page of camera-ready.
-\ificcvfinal\thispagestyle{empty}\fi
-
-%%%%%%%%% ABSTRACT
+%
+\titlerunning{Chest, wAist and peLVIS circumference from 3D human body meshes}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
+\author{Yansel Gonzalez Tejeda\orcidID{0000-0003-1002-3815} \and
+Helmut Mayer\orcidID{1111-2222-3333-4444}}
+%
+\authorrunning{Gonzalez and Mayer}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Paris Lodron University of 
+	Salzburg, Kapitelgasse 4-65020 Salzburg, Austria
+\url{https://www.uni-salzburg.at}}
+%
+\maketitle              % typeset the header of the contribution
+%
 \begin{abstract}
@@
 advance the field.
+
+\keywords{First keyword  \and Second keyword \and Another keyword.}
 \end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-
+%
+%
+%
 \textbf{Motivation} 
@@
 ground at shoulder height at a $90^\circ$ angle. In the line 
-of previous work (\cite{Dibra.2016a}), we name this pose the zero (also 
+of previous work \cite{Dibra.2016a}, we name this pose the zero (also 
 normalized (rf)) pose $\vec{\theta}^*$. Additionally, we assume that the mesh 
@@
 can formalize this intuition by considering the cross-sectional length of the 
-2D intersection curves (\cite{book.compu.topo}) along the y-axis. Moreover, we 
+2D intersection curves \cite{book.compu.topo} along the y-axis. Moreover, we 
 can 
@@
 \mathbb{R}$ as
-\begin{align}
+\begin{equation}
 \mathcal{BL}(\mathcal{M}, \boldsymbol{\pi}, j) = \sum_{i = 
 	1}^{i = n}s_i
-\end{align}
+\end{equation}
 
@@
 The method can be optimized. Further research must be conducted.
-
-{\small
-\bibliographystyle{ieee}
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+\bibliographystyle{splncs04}
 \bibliography{egbib}
-}
+%
 

### 2019-09-11 PaperRMFI2019/samplepaper.tex
update text

@@
 
-\keywords{First keyword  \and Second keyword \and Another keyword.}
+\keywords{Human Shape Estimation \and CNN \and Another keyword.}
 \end{abstract}
@@
 measurements (\cite{Sigal.2008}), body dimensions 
-(\cite{DBLP:conf/bmvc/ChenRC11}), semantical parameters (\cite{Yang.2014}), 
+(\cite{DBLP:conf/bmvc/ChenRC11}, European standard EN 13402), semantical 
+parameters (\cite{Yang.2014}), 
 traditional anthropometric 
@@
 In this work we synthesize 3D human meshes using the SMPL
-model \cite{Loper.2015}. This model is at its top level a skinned articulated 
+model \cite{Loper.2015}. The generative nature of our approach establishes this 
+model as starting point (and not the 3D mesh). Nevertheless, our method is 
+flexible enough to begin the pipeline with a 3D mesh. In that case, an SMPL 
+model can be fitted to it, using the method of (rh) for example.
+This model is at its top level a skinned articulated 
 model, i.e., 
@@
 at the widest part of the torso and the waist circumference at the 
-narrowest part after the chest but above the hips. Similarly, the pelvis 
-circumference is measured often around the widest part of hips and buttocks. We 
+narrowest part after the chest but above the hips. This intuition is compliant 
+with prior body dimensions standarised definitions (rf EN 13402 - 1). 
+Similarly, the pelvis 
+circumference is measured often (rf) around the widest part of hips and 
+buttocks. We 
 can formalize this intuition by considering the cross-sectional length of the 
@@
 general, we expect these \textit{extrema} to be adequate features to 
-calculate the human dimensions. More specifically, we assume that:
+calculate the human dimensions. However, there is no consensus in the 
+literature regarding the method to calculate chest, waist and hip 
+circumference. While Yansel et al., 2020 define waist circumference as the
+
+More specifically, we assume that:
 \begin{enumerate}
@@
 	it at two points left $p_l$ and right $p_r$.
+	\item The plane $\boldsymbol{\pi}$ intersects the mesh $\mathcal{M}$ at the 
+	point where the left hip is located defining a path. The length of this 
+	path is $P_{lh}$.	
 	\item The local maximum $M_{pc}$ with largest value other than $M_g$ 
-	immediately posterior to $p_r$ represents the pelvis circumference.
+	immediately prior to $P_{lh}$ represents the pelvis circumference.	
 	\item The local minimum $M_{wc}$ posterior to $p_r$ but prior to $M_{pc}$ 

### 2019-09-17 PaperRMFI2019/samplepaper.tex
more on calvis

@@
 \usepackage{amssymb}
+\usepackage{float}
 %
@@
 %
+\section{Introduction}\label{sec:intro}
 \textbf{Motivation} 
@@
 
-Problem statement: given a 3D human body mesh $\mathcal{M}$ we look for a 
+\textbf{Problem statement:} given a 3D human body mesh $\mathcal{M}$ we look 
+for a 
 method capable to automatically output chest, waist and pelvis circumference.
+
+\section{Related Work}\label{sec:rel_work}
 
@@
 \section{Approach}\label{sec:approach}
+To calculate the actual human body dimensions, we first need to formalize the 
+notion of chest, waist and pelvis of a 3D human body mesh. The starting point 
+is the model capable to represent that mesh, which we discuss in subsection 
+\ref{subsec:smpl_model}. Next, we define a mesh signature over that mesh in 
+subsection \ref{eq:mesh_signature} that allow us to formalize the human body 
+dimensions.
+Our strategy segmentates consist of segmentating the mesh torso in three 
+regions, namely chest, waist and pelvic regions. We then apply the formal 
+definitions and search for extrema and identify points in those regions that we 
+can interpret as the wanted body dimensions.
 
+\subsection{SMPL Model of the Human Body}\label{subsec:smpl_model}
 In this work we synthesize 3D human meshes using the SMPL
@@
 
+\subsection{Chest, Waist and Pelvis Regions 
+Segmentation}\label{subsec:three_regions}
+
+\subsubsection{Axilla recognition}\label{subsec:armpit_recog}
+As mentioned above, we would like to measure the chest circumference below the 
+armpit, also known as axilla. This raises the question whether we can recognize 
+the axilla based on 
+the mesh signature. We could then establish the location index as lower bound 
+for the search of chest location. There is consensus regarding the axilla 
+definition as the area of the human body underneath the shoulder joint 
+(\cite{MeSH.axilla}, \cite{FMA.axilla}, \cite{TA.axilla}). Therefore, we can 
+use the shoulder joint as a hint to locate the axilla and establish a lower 
+bound for the chest region. We then can combine this idea with the defintion 
+used in the garment industry, namely the maximum horizontal girth under the 
+armpits (axillae) (rh).
+Let us consider the left shoulder joint on in our skeleton model $J_{ls}$. We 
+cast a ray in direction $d$ outside the mesh. Since the joint $J_{ls}$ lies 
+inside the mesh, the ray intersects its surface at point $p_{axilla}$ (see 
+figure x).
+With this construction we can define the chest region $\mathcal{CR}$ as the 
+region where the slice index is bigger that the index of a slice with 
+y-coordinate is equal or greater than the axilla $y$-coordinate 
+$y_{p_{axilla}}$.
+
+\begin{align}
+\mathcal{CR} = \mathcal{BL}(j), \, j \in \{j_t, j_t+m, \cdots, j_b\}
+\end{align}
+
+Similarly, the waist region is
+
+\begin{align}
+\mathcal{WR} = \mathcal{BL}(j), \, j \in \{j_t, j_t+m, \cdots, j_b\}
+\end{align}
+
+Finally, the pelvic region is
+
+\begin{align}
+\mathcal{PR} = \mathcal{BL}(j), \, j \in \{j_t, j_t+m, \cdots, j_b\}
+\end{align}
+
+\subsection{Recognition by interval search}\label{subsec:interval_search}
+
 %------------------------------------------------------------------------
@@
 
+\subsection{Qualitative evaluation}\label{subsec:qualitative_eval}
+Here we evaluate our method qualitatively with method one and method two.
+\begin{figure}[H]
+	\begin{center}
+		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+		\includegraphics[width=\linewidth]{subject_6_with_cutting_planes_on_joints.eps}
+	\end{center}
+	\caption{Qualitative evaluation for male and female meshes. We evaluate our 
+	method with method one and method two.}
+	\label{fig:qualitative_eval}
+\end{figure}
+
+Figure \ref{fig:qualitative_eval} shows the $\mathcal{MS}$ of two meshes (male 
+and female) for 
+$m=0,001$ and plane $\boldsymbol{\pi}$ parallel to the floor (with normal $(0, 
+1,0)$) using the library trimesh \cite{trimesh}. Note that the function as 
+defined by equation \ref{eq:mesh_signature} is bounded and not continuous. It 
+resembles a rotated silhouette of the human body and exhibits several 
+\textit{extrema}.
+
+\begin{figure}[h]
+	\begin{center}
+		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+		\includegraphics[width=\linewidth]{Figure_1.eps}
+	\end{center}
+	\caption{Human Body Mesh Signature for male and female meshes. The 
+		function resembles a rotated silhouette of the human body and exhibits 
+		several \textit{extrema}. See section 
+		\ref{subsec:mesh_signature_extrema} for discussion of these extrema.}
+	\label{fig:qualitative_eval}
+\end{figure}
+
+\subsection{Learning convergence evaluation}\label{subsec:learn_conv}
+This experiment demonstrates the plausibility of using calvis to obtain data 
+that can be used as a ground truth for machine learning (in general) and 
+specifically as supervising signal for ANN.
+
+Figure \ref{fig:calvis_net} shows the our prototypical ANN calvis net where the 
+input is a synthetic image from a 3D mesh and the output are the three body 
+dimensions.
+
+Figure \ref{fig:learn_conv} shows that after epoch number 5 the estimation 
+error decreases and the learning converges.
+
+\begin{figure}[H]
+	\begin{center}
+		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+		\includegraphics[width=\linewidth]{Figure_1.eps}
+	\end{center}
+	\caption{Human Body Mesh Signature for male and female meshes. The 
+		function resembles a rotated silhouette of the human body and exhibits 
+		several \textit{extrema}. See section 
+		\ref{subsec:mesh_signature_extrema} for discussion of these extrema.}
+	\label{fig:qualitative_eval}
+\end{figure}
+
+\begin{figure}[H]
+	\begin{center}
+		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+		\includegraphics[width=\linewidth]{Figure_1.eps}
+	\end{center}
+	\caption{Human Body Mesh Signature for male and female meshes. The 
+		function resembles a rotated silhouette of the human body and exhibits 
+		several \textit{extrema}. See section 
+		\ref{subsec:mesh_signature_extrema} for discussion of these extrema.}
+	\label{fig:qualitative_eval}
+\end{figure}
+
 %------------------------------------------------------------------------

### 2019-09-23 PaperRMFI2019/samplepaper.tex
more on segmentation

@@
 %
-\documentclass[runningheads]{llncs}
+\documentclass[runningheads, orivec]{llncs}
 %
@@
 this data as ground truth for learning with convolutional neural networks 
-(CNN). Previous work had used the large scale CAESAR dataset, determined 
-$\textit{manually}$ these anthropometrical measurements or directly acquired 
-them from a person. The problem is that acquiring these data is a cost and 
+(CNN). Previous work had used the large scale CAESAR dataset or determined 
+$\textit{manually}$ these anthropometrical measurements directly from a person 
+or human 3D body meshes. 
+Unfortunately, acquiring these data is a cost and 
 time consuming endeavor. In contrast our method can be used on 
-3D meshes automatically. First, we slice cross sections along the Y axis of 
-the mesh. Second, we calculate the cross sections length and establish a 
-signature for the body represented by the mesh. Finally, using this 
-signature we are able to calculate the chest, waist and pelvis 
-circumference by searching for extrema. We conduct two experiments. 
+3D meshes automatically. We conduct two experiments. 
 In the first experiment we synthesize 10 human body meshes. Then we apply 
@@
 plausibility of our approach where we use the calculated human dimensions as 
-a ground truth to train a small CNN. After having trained the network with 
+a ground truth to train a small CNN. After 
+having trained the network with 
 our data, we demonstrate that learning converges, achieving $x$ percent 
@@
 
-\keywords{Human Shape Estimation \and CNN \and Another keyword.}
+\keywords{chest, waist and pelvis circumference \and 3D human body mesh \and 
+deep learning}
 \end{abstract}
@@
 named this 
-measurements body intuitive controls (\cite{Allen.2003}), biometric 
-measurements (\cite{Sigal.2008}), body dimensions 
-(\cite{DBLP:conf/bmvc/ChenRC11}, European standard EN 13402), semantical 
-parameters (\cite{Yang.2014}), 
+measurements body intuitive controls \cite{Allen.2003}, biometric 
+measurements \cite{Sigal.2008}, body dimensions 
+\cite{DBLP:conf/bmvc/ChenRC11}, (European standard EN 13402), semantical 
+parameters \cite{Yang.2014}, 
 traditional anthropometric 
 measurements 
-(\cite{Wuhrer2011}) or only ``shape" as in human shape estimation 
-(\cite{Guan.2013}, \cite{Bogo:ECCV:2016}, \cite{Loper.2015}, 
-\cite{Dibra.2016a}, \cite{Pishchulin.2017}). In contrast, we assume a more 
+\cite{Wuhrer2011} or only ``shape" as in human shape estimation 
+\cite{Guan.2013,Bogo:ECCV:2016,Loper.2015,Dibra.2016a,Pishchulin.2017}. In 
+contrast, we assume a more 
 anthropometric approach 
@@
 dimensions 
-will be used to refer to the above measurements.
+will be used to refer to the above measurements and we will focus on three of 
+these dimensions, namely chest, waist and 
+pelvis circumference.
 
-The problem of estimating human body dimensions  
-having only an image is an under-constrained  (or inverse) problem. Information 
+The problem of estimating chest, waist and 
+pelvis circumference having only an image of a person is a challenging problem 
+and involve recognizing the corresponding location of these dimension in the 
+body and estimating their circumference. Additionally, the setting is an  
+under-constrained  (or inverse) problem. Information 
 gets lost when a camera is 
@@
 
-\textbf{Problem statement:} given a 3D human body mesh $\mathcal{M}$ we look 
-for a 
-method capable to automatically output chest, waist and pelvis circumference.
+\textbf{Contributions} In summary, our contributions are $1)$ CALVIS: a method 
+capable of automatically outputting chest, waist and pelvis circumference from 
+3D body meshes. $2)$ A prototype deep learning framework (CNN) with synthetic 
+images of 3D human body meshes as input and the human body dimension obtained 
+with CALVIS as supervision signal.
 
@@
 
+\subsection{Human Body Data synthesis}
+The \cite{Anguelov.2005} SCAPE model opened wide possibilities in the field  
+because it provided the community with a generative model of the human 
+body. However, if (Problem they address) (which method?)(Results?) (Open 
+Problems).
+After some(which, reference here) attempts on improving (say here either 
+quality or spped), Loper et al., 2018 \cite{Loper.2015} developed a generative 
+human body model.(Problem they address) (which method?)(Results?) (Open 
+Problems).
+Pischchulin et al., 2017 \cite{Pishchulin.2017} synthesize data. (Problem they 
+address) (which method?)(Results?) (Open Problems).
+More recently, Joo et al. \cite{Joo.2018} presents a human model with SMPL as a 
+body model and added hand and face. We do not use that more complex model in 
+this paper, that is future work.
+
+\subsection{Human Body Dimensions from 3D models}
+Allen et al., 2003 \cite{Allen.2003} proposed how to relate what they call body 
+intuitive controls, e.g. height, weight, age and sex with PCAs performed on the 
+space X (replace X!) using a linear mapping. Describe more please! (Problems)- 
+make connection to next related work.  
+Sigal et al., 2008 \cite{Sigal.2008} used a generative model (which method?) to 
+estimate what he calls biometric measurements. (Results?) (Open Problems).
+It is obvious that the problem of estimating the shape and pose of a human 
+having only an image it is an under-constrained  (or inverse) problem. 
+\cite{Guan.2013}  argues that (why) this situation can be alleviated by 
+providing the shape model with the capability of keeping the height constant. 
+This is indeed not the case for the original SCAPE model because the height is 
+a semantical parameter and semantical parameters are “spread” over all bases. 
+The arguments goes like this: SCAPE is a good human shape model. At its core 
+this model relates triangles deformations to semantical parameters. One of the 
+first problem one encounters when trying to model the human shape is the model 
+size: because one needs a lot (~6000) triangles to sculpt a human body, you 
+have the same amount of dimensions. Then one applies dimensionality reduction 
+techniques, in this case PCA, having at the end around 20 components. These 
+components do not describe intuitively (are not expressed explicit in the model 
+) human shape characteristics (e.g., height, chest circumference or waist), 
+nevertheless they are the bases of a vector space containing human shapes. Next 
+\cite{Guan.2013} goes an argue that by “rotating” one (or more) of these bases 
+we can vary the other bases  without being forced to vary the height.
+
+Wuhrer and Shu, 2013 \cite{Wuhrer.2013} proposed a method to 
+create/estimate/generate 3D human shapes from traditional anthropometric 
+measurements. They learned a correlation between the 3D bodies meshes and 1D 
+measurements. Then, when predicting a new shape, they find an initial solution 
+based on the learned correlation (yansel WHICH correlation) and refine this 
+solution by a two-step non linear optimization. They build up on two 
+assumptions, namely, that the initial estimation should be in the plausible 
+space of human shapes and second, that, in order to generalized, the model has 
+to be refined without using this prior knowledge. While the first step use 
+information from the learned shape prior, the second step introduce a 
+smoothness constraint on the objective function. Like this work we use a set of 
+traditional anthropometric measurements, unlike them we calculate 1D 
+measurements from 3D human bodies to use them as ground truth for later 
+inference. Their approach is able to capture variation outside the shape space 
+spanned by the training data, in other words, the approach generalized well.
+At the same time, Boisvert et al., 2013 \cite{Boisvert.2013} estimate human 
+shape from measurements (what is that)(which method?)(Results?) (Open 
+Problems). These two works can not be directly quantitatively compared because 
+they use different set of measurements.
+Moreover, Yang et al., 2014 \cite{Yang.2014} developed a method to map 
+principal component to what they call semantical parameters. These semantical 
+parameter are indeed anthropometric measurements, which justify their naming: 
+in contrast to anthropometric meaningless principal components, their model is 
+capable of manipulating concepts like chest and waist 
+circumference.(Method?)(Results?).   
+Tsoli et al., 2014 \cite{Tsoli.2014} extract what they calls anthropometric or 
+tailored measurements introduced model-based anthropometry (what is that)(which 
+method?)(Results?) (Open Problems).
+
+\subsection{Human Shape Estimation with Artificial Neural Networks}
+A huge amount of research has been conducted in recent years to address the 
+problem of 3D/2D human shape estimation using ANNs. Experimented with different 
+architectures.
+An state-of-the-art method is \cite{kanazawaHMR18} where they estimate human 
+shape and pose.
+
 %------------------------------------------------------------------------
 \section{Approach}\label{sec:approach}
-To calculate the actual human body dimensions, we first need to formalize the 
-notion of chest, waist and pelvis of a 3D human body mesh. The starting point 
-is the model capable to represent that mesh, which we discuss in subsection 
-\ref{subsec:smpl_model}. Next, we define a mesh signature over that mesh in 
-subsection \ref{eq:mesh_signature} that allow us to formalize the human body 
-dimensions.
-Our strategy segmentates consist of segmentating the mesh torso in three 
-regions, namely chest, waist and pelvic regions. We then apply the formal 
-definitions and search for extrema and identify points in those regions that we 
-can interpret as the wanted body dimensions.
+While human body 
+meshes are traditionally acquired by specialized 3D scanners, we use a 
+generative model to synthesize them, which we briefly review in 
+subsection \ref{subsec:smpl_model}. To calculate the actual human body 
+dimensions, we first need to formalize the 
+notion of chest, waist and pelvis of a 3D human body mesh. Our strategy consist 
+of segmentating the mesh in five regions, 
+three of them of interest, which we 
+discuss in subsection \ref{subsec:three_regions}. Finally, within these regions 
+we identify the intended dimensions employing a human body mesh signature 
+(HBMS), 
+defined in subsection \ref{subsec:hbm_signature}.
 
-\subsection{SMPL Model of the Human Body}\label{subsec:smpl_model}
+\subsection{SMPL Generative Model of the Human Body}\label{subsec:smpl_model}
 In this work we synthesize 3D human meshes using the SMPL
@@
 flexible enough to begin the pipeline with a 3D mesh. In that case, an SMPL 
-model can be fitted to it, using the method of (rh) for example.
-This model is at its top level a skinned articulated 
+model can be fitted to the volumetric data, using the method described by 
+Varol et al., 2018 \cite{varol18_bodynet} for example.
+
+The SMPL model is at its top level a skinned articulated 
 model, i.e., 
 consists of a 
-surface mesh that mimics the skin and a skeleton related to that mesh. It is 
-defined by a mean 
-template shape represented by a vector of $N$ concatenated vertices 
-$\mathbf{\bar{T}}$ in the zero pose, $\vec{\theta}^*$. In order 
-to 
-synthesize a 
-new human mesh one has to deform the provided template mesh by 
-setting shape parameters $\vec{\beta}$ and pose parameters $\vec{\theta}$. The 
+surface mesh $\mathcal{M}$ that mimics the skin and a corresponding skeleton 
+$\mathbf{J}$. The mesh $\mathcal{M} \in \mathbb{R}^{3N}$, which is a boundary 
+representation stores 
+both the body geometry (vertex position) and topology (how the vertices are 
+connected). The skeleton $\mathbf{J}$ is defined by its endpoints (joints) 
+location in 3D space $j_i \in \mathbb{R}^3$  and its kinematic tree. Two 
+connected 
+joints define a 'bone' $P_i$. Moreover, a child bone is rotated relative to its 
+connected parent. The pose $\vec{\theta}$ is the specification of every bone 
+rotation in angle-axis form plus an orientation for the root bone.
+
+More specifically, the SMPL model is defined by a template mesh (mean template 
+shape) $\mathbf{\bar{T}}$ represented by a vector of $N = 6890$ concatenated 
+vertices in the zero pose, $\vec{\theta}^*$. The skeleton has $K = 23$ joints, 
+therefore a pose vector is defined by $|\vec{\theta}| = 3 \times 23 + 3 = 72$ 
+parameters. In order 
+to synthesize a new human mesh one has to deform the 
+provided template mesh by 
+setting shape parameters $\vec{\beta}$. Pose parameters $\vec{\theta}$ are used 
+for animation. 
+The 
 model provides learned parameters
@@
 \Phi = \{\mathbf{\bar{T}}, \mathcal{W}, \mathcal{S}, \mathcal{J}, 
-\mathcal{P}\}
+\mathcal{P}\}.
 \end{equation}
-As mentioned above $\mathbf{\bar{T}}$ is the mean template shape. The weight 
-matrix $\mathcal{W}$ represents how much the rotation of skeleton parts affects 
+
+As mentioned above $\mathbf{\bar{T}} \in \mathbb{R}^{3N}$  is the mean template 
+shape. The set of blend weights $\mathcal{W} \in \mathbb{R}^{N \times K}$ 
+represents 
+how much the rotation of 
+skeleton bones affects
 the vertices. In addition, the matrices $\mathcal{S}$ and $\mathcal{P}$ define 
-linear functions that are used to deform $\mathbf{\bar{T}}$ and the matrix 
-$\mathcal{J}$ predicts skeleton rest joint locations from vertices in the rest 
-pose. We held fix these parameters during the synthesis.
+respectively linear functions $B_s(\vec{\beta}; \mathcal{S}): 
+\mathbb{R}^{|\vec{\beta}|} \to 
+\mathbb{R}^{3N}$ and $B_p(\vec{\theta}; \mathcal{P}): 
+\mathbb{R}^{|\vec{\theta}|} \to 
+\mathbb{R}^{3N}$ that are used to deform $\mathbf{\bar{T}}$; and the function 
+$\mathcal{J}: \mathbb{R}^{|\vec{\beta}|} \to \mathbb{R}^{3K}$ predicts skeleton 
+rest joint locations from vertices in the rest 
+pose. A new mesh $\mathcal{M}_{new}$ can be then generated
 
-\subsection{Human Body Mesh Signature}\label{subsec:hbm_signature}
+\begin{equation}\label{eq:gen_mesh}
+\mathcal{M}_{new} = M(\vec{\beta}, \vec{\theta}, \Phi).
+\end{equation}
+
+Since we held fix parameters $\Phi$ during the synthesis and either we change 
+$\vec{\theta}$ because our approach focuses on the zero pose $\vec{\theta}^*$, 
+we manufacture a new mesh
+
+\begin{equation}\label{eq:gen_mesh_only_shape}
+\mathcal{M}_{new} = M(\vec{\beta}).
+\end{equation}
+
+\begin{equation}\label{eq:gen_new_mesh}
+\mathcal{M}_{new} = \mathbf{\bar{T}} + B_s(\vec{\beta}; \mathcal{S}).
+\end{equation}
+
+As a result we obtain a mesh that realistically represents a human body. Next, 
+we focus on establishing reasonable chest, waist and pelvis regions on this 
+mesh.
+
+\subsection{Chest, Waist and Pelvic Regions 
+Segmentation}\label{subsec:three_regions}
+
 Let us consider a human body mesh $\mathcal{M}$. Our method requires that 
@@
 parallel to the 
-ground at shoulder height at a $90^\circ$ angle. In the line 
-of previous work \cite{Dibra.2016a}, we name this pose the zero (also 
-normalized (rf)) pose $\vec{\theta}^*$. Additionally, we assume that the mesh 
+ground at shoulder height at a $90^\circ$ angle (SMPL normalized pose
+$\vec{\theta}^*$). Additionally, we assume that the mesh 
 has LSA orientation, e.g., x, y and z axis are positively directed from 
@@
 
-Intuitively, we would like to measure the chest circumference bellow the arms 
-at the widest part of the torso and the waist circumference at the 
-narrowest part after the chest but above the hips. This intuition is compliant 
-with prior body dimensions standarised definitions (rf EN 13402 - 1). 
-Similarly, the pelvis 
-circumference is measured often (rf) around the widest part of hips and 
-buttocks. We 
-can formalize this intuition by considering the cross-sectional length of the 
-2D intersection curves \cite{book.compu.topo} along the y-axis. Moreover, we 
-can 
-use a plane $\boldsymbol{\pi}$ parallel to the floor to intersect the mesh. 
-Since $\mathcal{M}$ is 
-triangulated, the boundary of this 
-intersection is a collection of segments $s_i$. Therefore, we can 
-determine the boundary length by specifying a point along the y-axis $j \in 
-\mathbb{R}$ as
-\begin{equation}
-\mathcal{BL}(\mathcal{M}, \boldsymbol{\pi}, j) = \sum_{i = 
-	1}^{i = n}s_i
-\end{equation}
+We observe that the chest circumference is usually measure bellow the armpits, 
+also 
+known as axilla, but above the natural waist. Similarly, the pelvis 
+circumference is measured often around the hips. This observation suggests that 
+we should consider segmenting the mesh in meaningful regions. Moreover, we can 
+use the skeleton when determining the region boundaries. For 
+example, there is consensus regarding the axilla 
+definition as the area of the human body underneath the shoulder joint 
+(\cite{MeSH.axilla}, \cite{FMA.axilla}, \cite{TA.axilla}). Therefore, we can 
+use the shoulder joint as a hint to locate the axilla and establish a upper 
+bound for the chest region. More generally, we can use the 
+skeleton joints defined in $\mathbf{J}$ to identify the regions boundaries.
 
-Note that for cross sections where $\boldsymbol{\pi}$ intersects the legs, two 
-disconnected curves will appear. That is by no means a problem because they are 
-still a collection of segment with non-zero length.
-
-\begin{figure}[t]
-	\begin{center}
-		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-		\includegraphics[width=\linewidth]{Figure_1.eps}
-	\end{center}
-	\caption{Human Body Mesh Signature for male and female meshes. The 
-		function resembles a rotated silhouette of the human body and exhibits 
-		several \textit{extrema}. See section 
-		\ref{subsec:mesh_signature_extrema} for discussion of these extrema.}
-	\label{fig:hbm_signature}
-\end{figure}
-
-Next, we assemble the mesh slide length vector $\vec{\mathcal{L}}$. Starting 
-from the 
-top $j_t$ of the bounding box we sliced iterative mesh $\mathcal{M}$ with plane 
-$\boldsymbol{\pi}$ every $m$-meters until we reach the bounding box bottom 
-$j_b$. For every slice at point $j$, we compute $\mathcal{BL}(j)$.
+Recall that mesh $\mathcal{M}$ has $N$ vertices. Let the set of vertices be 
+$\mathcal{V}$ and $j^y_i$ the y-coordinate of vertex $j_i$, we can segment the 
+mesh in chest, waist and pelvic regions 
+$\mathcal{CR}, \mathcal{WR}, \mathcal{PR}$, respectively
 
 \begin{align}
-\vec{\mathcal{L}}(\mathcal{M}, \boldsymbol{\pi}, m) = \mathcal{BL}(j), \, j 
-\in 
-\{j_t, j_t+m, \cdots, j_b\}
+\mathcal{CR} = \mathcal{BL}(j), \, j \in \{j_t, j_t+m, \cdots, j_b\}
 \end{align}
 
-Finally, we can construct the human body \textbf{mesh signature} $\mathcal{MS}: 
-\mathbb{Z}^+ \to \mathbb{R}$ that maps every slice index $k \in \{0, 1, \cdots, 
-|\mathcal{L}|-1\}$ to the corresponding boundary length $\mathcal{BL}(j)$ in 
-the mesh slide vector $\vec{\mathcal{L}}$.
-
-\begin{align}\label{eq:mesh_signature}
-\mathcal{MS}(k) = \mathcal{BL}(j)
+\begin{align}
+\mathcal{WR} = \mathcal{BL}(j), \, j \in \{j_t, j_t+m, \cdots, j_b\}
 \end{align}
 
-Figure \ref{fig:hbm_signature} shows the $\mathcal{MS}$ of two meshes (male 
-and female) for 
-$m=0,001$ and plane $\boldsymbol{\pi}$ parallel to the floor (with normal $(0, 
-1,0)$) using the library trimesh \cite{trimesh}. Note that the function as 
-defined by equation \ref{eq:mesh_signature} is bounded and not continuous. It 
-resembles a rotated silhouette of the human body and exhibits several 
-\textit{extrema}.
-
-\subsection{Mesh Signature Extrema}\label{subsec:mesh_signature_extrema}
-
-By comparing neighboring values of the mesh signature $\mathcal{MS}$ as defined 
-in equation \ref{eq:mesh_signature} we find several \textit{extrema}. In 
-general, we expect these \textit{extrema} to be adequate features to 
-calculate the human dimensions. However, there is no consensus in the 
-literature regarding the method to calculate chest, waist and hip 
-circumference. While Yansel et al., 2020 define waist circumference as the
-
-More specifically, we assume that:
-\begin{enumerate}
-	\item The global maximum $M_g$ represents the length of the largest path 
-	around the arms. From a topographic point of view $M_g$ is the highest peak 
-	of $\mathcal{MS}$. A horizontal line at height proportion $h$ of the peak 
-	intersects 
-	it at two points left $p_l$ and right $p_r$.
-	\item The plane $\boldsymbol{\pi}$ intersects the mesh $\mathcal{M}$ at the 
-	point where the left hip is located defining a path. The length of this 
-	path is $P_{lh}$.	
-	\item The local maximum $M_{pc}$ with largest value other than $M_g$ 
-	immediately prior to $P_{lh}$ represents the pelvis circumference.	
-	\item The local minimum $M_{wc}$ posterior to $p_r$ but prior to $M_{pc}$ 
-	represents waist circumference.
-	\item The local maximum $M_{cc}$ posterior to $p_r$ but prior to $M_{wc}$ 
-	represents 
-	chest circumference. If this local maximum does not exist we set $M_{cc}$ 
-	to the value of the path $\mathcal{BL}(j_{cc})$ with largest value in the 
-	interval $(p_l; M_{wc})$.
-\end{enumerate}
-
-\subsection{Chest, Waist and Pelvis Regions 
-Segmentation}\label{subsec:three_regions}
+\begin{align}
+\mathcal{PR} = \mathcal{BL}(j), \, j \in \{j_t, j_t+m, \cdots, j_b\}
+\end{align}
 
@@
 \end{align}
+
+\subsection{Human Body Mesh Signature}\label{subsec:hbm_signature}
+Intuitively, we would like to measure the chest circumference bellow the arms 
+at the widest part of the torso and the waist circumference at the 
+narrowest part after the chest but above the hips. This intuition is compliant 
+with prior body dimensions standardized definition, for example the European 
+standard EN 13402-1. Similarly, the pelvis 
+circumference is measured often around the widest part of hips and 
+buttocks. We 
+can formalize this intuition by considering the cross-sectional length of the 
+2D intersection curves\cite{book.compu.topo} along the y-axis. Moreover, we 
+can 
+use a plane $\boldsymbol{\pi_j}$ parallel (with normal $\vec{n}_{||}$) to the 
+floor to intersect the mesh at a point $j \in 
+\mathbb{R}$ along the y-axis. Since $\mathcal{M}$ is triangulated, the boundary 
+of this 
+intersection is a collection of segments $s_i$. Therefore, we can 
+determine the intersection boundary length as
+\begin{equation}
+\mathcal{BL}(\mathcal{M}, \vec{n}_{||}, j) = \sum_{i = 
+	1}^{i = N}s_i
+\end{equation}
+
+Note that for cross sections where $\boldsymbol{\pi_j}$ intersects the legs, 
+two 
+disconnected curves will appear. This is not necessarily a problem, because a 
+set of disconnected curves has non-zero length (rf?).
+
+\begin{figure}[t]
+	\begin{center}
+		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+		\includegraphics[width=\linewidth]{Figure_1.eps}
+	\end{center}
+	\caption{Human Body Mesh Signature for male and female meshes. The 
+		function resembles a rotated silhouette of the human body and exhibits 
+		several \textit{extrema}. See section 
+		\ref{subsec:mesh_signature_extrema} for discussion of these extrema.}
+	\label{fig:hbm_signature}
+\end{figure}
+
+Next, we assemble the mesh slide length vector $\vec{\mathcal{L}}$. Starting 
+from the 
+top $j_t$ of the bounding box we slice iteratively mesh $\mathcal{M}$ with 
+plane 
+$\boldsymbol{\pi_j}$ every $m$-meters until we reach the bounding box bottom 
+$j_b$. Because the mesh $\mathcal{M}$ and the plane normal $\vec{n}_{||}$ 
+remains the same we can drop them from the notation. For every slice at point 
+$j$, we compute $\mathcal{BL}(j)$.
+
+\begin{align}
+\vec{\mathcal{L}}(\mathcal{M}, \vec{n}_{||}, m) = \left[ \mathcal{BL}(j_t), 
+\mathcal{BL}(j_t+m), \cdots, \mathcal{BL}(j_b) \right]
+\end{align}
+
+Finally, we can define the human body \textbf{mesh signature} $\mathcal{MS}: 
+\mathbb{Z}^+ \to \mathbb{R}$ that maps every slice index $k \in \{0, 1, \cdots, 
+|\mathcal{L}|-1\}$ to the corresponding boundary length $\mathcal{BL}(j)$ in 
+the mesh slide vector $\vec{\mathcal{L}}$.
+
+\begin{align}\label{eq:mesh_signature}
+\mathcal{MS}(k) = \mathcal{BL}(j)
+\end{align}
+
+Figure \ref{fig:hbm_signature} shows the $\mathcal{MS}$ of two meshes (male 
+and female) for 
+$m=0,001$ and plane $\boldsymbol{\pi}$ parallel to the floor (with normal $(0, 
+1,0)$) using the library trimesh \cite{trimesh}. Note that the function as 
+defined by equation \ref{eq:mesh_signature} is bounded and not continuous. It 
+resembles a rotated silhouette of the human body and exhibits several 
+\textit{extrema}.
+
+In general, we expect these \textit{extrema} to be adequate features to 
+calculate the human dimensions. However, there is no consensus in the 
+literature regarding the method to calculate chest, waist and hip 
+circumference. While Yansel et al., 2020 define waist circumference as the 
+blalal. That is why we first establish the regions and the search for local 
+extrema in these regions.
+
+More specifically, we assume that:
+\begin{enumerate}
+	\item The global maximum $M_g$ represents the length of the largest path 
+	around the arms. From a topographic point of view $M_g$ is the highest peak 
+	of $\mathcal{MS}$. A horizontal line at height proportion $h$ of the peak 
+	intersects 
+	it at two points left $p_l$ and right $p_r$.
+	\item The plane $\boldsymbol{\pi}$ intersects the mesh $\mathcal{M}$ at the 
+	point where the left hip is located defining a path. The length of this 
+	path is $P_{lh}$.	
+	\item The local maximum $M_{pc}$ with largest value other than $M_g$ 
+	immediately prior to $P_{lh}$ represents the pelvis circumference.	
+	\item The local minimum $M_{wc}$ posterior to $p_r$ but prior to $M_{pc}$ 
+	represents waist circumference.
+	\item The local maximum $M_{cc}$ posterior to $p_r$ but prior to $M_{wc}$ 
+	represents 
+	chest circumference. If this local maximum does not exist we set $M_{cc}$ 
+	to the value of the path $\mathcal{BL}(j_{cc})$ with largest value in the 
+	interval $(p_l; M_{wc})$.
+\end{enumerate}
 

### 2019-09-25 PaperRMFI2019/samplepaper.tex
add EN standard

@@
 
-The SMPL model is at its top level a skinned articulated 
-model, i.e., 
+The SMPL model is at its top level a \textbf{skinned articulated 
+model}, i.e., 
 consists of a 
@@
 both the body geometry (vertex position) and topology (how the vertices are 
-connected). The skeleton $\mathbf{J}$ is defined by its endpoints (joints) 
-location in 3D space $j_i \in \mathbb{R}^3$  and its kinematic tree. Two 
+connected). The skeleton $\mathbf{J}$ is defined by its joints location in 3D 
+space $j_i \in \mathbb{R}^3$  and its kinematic tree. Two 
 connected 
-joints define a 'bone' $P_i$. Moreover, a child bone is rotated relative to its 
+joints define a `bone'. Moreover, a child bone is rotated relative to 
+its 
 connected parent. The pose $\vec{\theta}$ is the specification of every bone 
-rotation in angle-axis form plus an orientation for the root bone.
+rotation plus an orientation for the root bone.
 
-More specifically, the SMPL model is defined by a template mesh (mean template 
-shape) $\mathbf{\bar{T}}$ represented by a vector of $N = 6890$ concatenated 
-vertices in the zero pose, $\vec{\theta}^*$. The skeleton has $K = 23$ joints, 
-therefore a pose vector is defined by $|\vec{\theta}| = 3 \times 23 + 3 = 72$ 
-parameters. In order 
-to synthesize a new human mesh one has to deform the 
-provided template mesh by 
+The SMPL model is also a \textbf{deformable model} 
+\cite{Terzopoulos:1987:EDM:37401.37427}. In order to 
+synthesize a 
+new human mesh one has to deform the provided template mesh by 
 setting shape parameters $\vec{\beta}$. Pose parameters $\vec{\theta}$ are used 
 for animation.
-The 
-model provides learned parameters
+
+More specifically, the model is defined by a template mesh (mean template 
+shape) $\mathbf{\bar{T}}$ represented by a vector of $N = 6890$ concatenated 
+vertices in the zero pose, $\vec{\theta}^*$. The skeleton has $K = 23$ joints.
+
+As an \textbf{statistical model}, SMPL provides learned parameters
 \begin{equation} \label{eq:smpl_params}
@@
 
+Let the axilla location be the point $p = (p^x, p^y, p^z)$ and 
+$j_{nw}$, $j_{pl}$, 
+$j_{lh} \in \mathbf{J}$ be the natural waist, pelvis and left hip joints, 
+respectively.
+
 Recall that mesh $\mathcal{M}$ has $N$ vertices. Let the set of vertices be 
-$\mathcal{V}$ and $j^y_i$ the y-coordinate of vertex $j_i$, we can segment the 
+$\mathcal{V}$ and $v^y_i$ the y-coordinate of vertex $v_i$, we can 
+segment the 
 mesh in chest, waist and pelvic regions 
@@
 
-\begin{align}
-\mathcal{CR} = \mathcal{BL}(j), \, j \in \{j_t, j_t+m, \cdots, j_b\}
+\begin{align}\label{eq:cr}
+\mathcal{CR} = \big(v^y_i \, | \, p^y > v^y_i \geq j^y_{nw} \big)
 \end{align}
 
-\begin{align}
-\mathcal{WR} = \mathcal{BL}(j), \, j \in \{j_t, j_t+m, \cdots, j_b\}
+\begin{align}\label{eq:wr}
+\mathcal{WR} = \big(v^y_i \, | \, j^y_{nw} > v^y_i \geq j_{pl}\big)
 \end{align}
 
-\begin{align}
-\mathcal{PR} = \mathcal{BL}(j), \, j \in \{j_t, j_t+m, \cdots, j_b\}
+\begin{align}\label{eq:pr}
+\mathcal{PR} = \big(v^y_i \, | \, j_{pl} > v^y_i \geq j_{lh}\big)
 \end{align}
@@
 armpit, also known as axilla. This raises the question whether we can recognize 
-the axilla based on 
-the mesh signature. We could then establish the location index as lower bound 
-for the search of chest location. There is consensus regarding the axilla 
-definition as the area of the human body underneath the shoulder joint 
-(\cite{MeSH.axilla}, \cite{FMA.axilla}, \cite{TA.axilla}). Therefore, we can 
-use the shoulder joint as a hint to locate the axilla and establish a lower 
-bound for the chest region. We then can combine this idea with the defintion 
-used in the garment industry, namely the maximum horizontal girth under the 
-armpits (axillae) (rh).
-Let us consider the left shoulder joint on in our skeleton model $J_{ls}$. We 
-cast a ray in direction $d$ outside the mesh. Since the joint $J_{ls}$ lies 
-inside the mesh, the ray intersects its surface at point $p_{axilla}$ (see 
+the axilla. What we want is a point in the mesh at the proper location under 
+the arms. One point suffices because we require only a reference along the 
+y-axis to define the chest region according to equation \ref{eq:cr}. Therefore, 
+we focus on the left shoulder joint $j_{ls} \in \mathbf{J}$. Since the axilla 
+is related to 
+the shoulder joint, we can cast a ray in direction $d$ outside the mesh. The 
+joint $j_{ls}$ lies inside the mesh thus the ray intersects its surface at 
+point $p$ (see 
 figure x).
-With this construction we can define the chest region $\mathcal{CR}$ as the 
-region where the slice index is bigger that the index of a slice with 
-y-coordinate is equal or greater than the axilla $y$-coordinate 
-$y_{p_{axilla}}$.
 
-\begin{align}
-\mathcal{CR} = \mathcal{BL}(j), \, j \in \{j_t, j_t+m, \cdots, j_b\}
-\end{align}
-
-Similarly, the waist region is
-
-\begin{align}
-\mathcal{WR} = \mathcal{BL}(j), \, j \in \{j_t, j_t+m, \cdots, j_b\}
-\end{align}
-
-Finally, the pelvic region is
-
-\begin{align}
-\mathcal{PR} = \mathcal{BL}(j), \, j \in \{j_t, j_t+m, \cdots, j_b\}
-\end{align}
+Once we have a segmented mesh, we search the dimensions within 
+these regions. The body dimensions we want to calculate are 
+geodesic on the mesh. Next subsection discuss how.
 
@@
 Intuitively, we would like to measure the chest circumference bellow the arms 
-at the widest part of the torso and the waist circumference at the 
-narrowest part after the chest but above the hips. This intuition is compliant 
-with prior body dimensions standardized definition, for example the European 
-standard EN 13402-1. Similarly, the pelvis 
+at the \textit{widest} part of the torso and the waist circumference at the 
+\textit{narrowest} part after the chest but above the hips. This intuition is 
+compliant 
+with prior body dimensions standardized definition, for example, the European 
+standard EN 13402-1 \cite{en13402-1}. Similarly, the pelvis 
 circumference is measured often around the widest part of hips and 
@@
 use a plane $\boldsymbol{\pi_j}$ parallel (with normal $\vec{n}_{||}$) to the 
-floor to intersect the mesh at a point $j \in 
+floor to intersect the mesh at a point $q \in 
 \mathbb{R}$ along the y-axis. Since $\mathcal{M}$ is triangulated, the boundary 
@@
 \begin{equation}
-\mathcal{BL}(\mathcal{M}, \vec{n}_{||}, j) = \sum_{i = 
+\mathcal{BL}(\mathcal{M}, \vec{n}_{||}, q) = \sum_{i = 
 	1}^{i = N}s_i
@@
 from the 
-top $j_t$ of the bounding box we slice iteratively mesh $\mathcal{M}$ with 
+top $q_t$ of the bounding box we slice iteratively mesh $\mathcal{M}$ with 
 plane 
 $\boldsymbol{\pi_j}$ every $m$-meters until we reach the bounding box bottom 
-$j_b$. Because the mesh $\mathcal{M}$ and the plane normal $\vec{n}_{||}$ 
+$q_b$. Because the mesh $\mathcal{M}$ and the plane normal $\vec{n}_{||}$ 
 remains the same we can drop them from the notation. For every slice at point 
-$j$, we compute $\mathcal{BL}(j)$.
+$q$, we compute $\mathcal{BL}(q)$.
 
 \begin{align}
-\vec{\mathcal{L}}(\mathcal{M}, \vec{n}_{||}, m) = \left[ \mathcal{BL}(j_t), 
-\mathcal{BL}(j_t+m), \cdots, \mathcal{BL}(j_b) \right]
+\vec{\mathcal{L}}(\mathcal{M}, \vec{n}_{||}, m) = \left[ \mathcal{BL}(q_t), 
+\mathcal{BL}(q_t+m), \cdots, \mathcal{BL}(q_b) \right]
 \end{align}
@@
 \mathbb{Z}^+ \to \mathbb{R}$ that maps every slice index $k \in \{0, 1, \cdots, 
-|\mathcal{L}|-1\}$ to the corresponding boundary length $\mathcal{BL}(j)$ in 
+|\mathcal{L}|-1\}$ to the corresponding boundary length $\mathcal{BL}(q)$ in 
 the mesh slide vector $\vec{\mathcal{L}}$.
@@
 \begin{align}\label{eq:mesh_signature}
-\mathcal{MS}(k) = \mathcal{BL}(j)
+\mathcal{MS}(k) = \mathcal{BL}(q)
 \end{align}
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
 	\begin{center}

### 2019-09-27 PaperRMFI2019/samplepaper.tex
axilla recognition

@@
 The SMPL model is also a \textbf{deformable model} 
-\cite{Terzopoulos:1987:EDM:37401.37427}. In order to 
+\cite{Terzopoulos.1987}. In order to 
 synthesize a 
@@
 
+\begin{figure}[t]
+	\begin{center}
+		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+		\includegraphics[width=\linewidth]{subjects_2_6_calvis_segmented.png}
+	\end{center}
+	\caption{Mesh segmentation in chest (red), waist (green) and pelvic (blue) 
+	regions. We show male (left) and female (right) subjects in frontal and 
+	lateral view.}
+	\label{fig:axilla-recognition}
+\end{figure}
+
 We observe that the chest circumference is usually measure bellow the armpits, 
-also 
-known as axilla, but above the natural waist. Similarly, the pelvis 
+also known as axilla, but above the natural waist. Similarly, the pelvis 
 circumference is measured often around the hips. This observation suggests that 
@@
 
-Let the axilla location be the point $p = (p^x, p^y, p^z)$ and 
+Let the axilla location be the point $p_a = (p^x_a, p^y_a, p^z_a)$ and 
 $j_{nw}$, $j_{pl}$, 
@@
 \begin{align}\label{eq:cr}
-\mathcal{CR} = \big(v^y_i \, | \, p^y > v^y_i \geq j^y_{nw} \big)
+\mathcal{CR} = \big(v^y_i \, | \, p^y_a > v^y_i \geq j^y_{nw} \big)
 \end{align}
@@
 \begin{align}\label{eq:wr}
-\mathcal{WR} = \big(v^y_i \, | \, j^y_{nw} > v^y_i \geq j_{pl}\big)
+\mathcal{WR} = \big(v^y_i \, | \, j^y_{nw} > v^y_i \geq j^y_{pl}\big)
 \end{align}
@@
 \begin{align}\label{eq:pr}
-\mathcal{PR} = \big(v^y_i \, | \, j_{pl} > v^y_i \geq j_{lh}\big)
+\mathcal{PR} = \big(v^y_i \, | \, j^y_{pl} > v^y_i \geq j^y_{lh}\big)
 \end{align}
@@
 is related to 
-the shoulder joint, we can cast a ray in direction $d$ outside the mesh. The 
-joint $j_{ls}$ lies inside the mesh thus the ray intersects its surface at 
-point $p$ (see 
-figure x).
+the shoulder joint, we can cast a ray $\boldsymbol{\iota}$ from it in direction 
+to the middle left 
+inferior edge of the bounding box outside the mesh at point
+
+\begin{align}
+p_b = \bigg(v^x_{min}, v^y_{min}, v^z_{min} + 
+\frac{v^z_{max} - v^z_{min}}{2}\bigg).
+\end{align}
+
+Here $v^x_{min}, v^y_{min}, v^z_{min}$ are vertex with minimum $x$,$y$ and $z$ 
+coordinates, respectively. Distance $d(v^z_{max},v^z_{min})$ is the euclidean 
+distance between vertices with maximum and minimum $z$ coordinate (figure x).
 
@@
 geodesic on the mesh. Next subsection discuss how.
+
+\begin{figure}[H]
+	\begin{center}
+		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+		\includegraphics[width=\linewidth]{axilla_recognition_final.png}
+	\end{center}
+	\caption{Axilla recognition based on the skeleton joint. We cast a ray from 
+	the left shoulder joint in direction to the middle left 
+		inferior edge of the bounding box (left). The ray intersects the mesh 
+		at point $p_a$ that we consider the axilla center. We plot the 10 
+		nearest vertices to $p_a$ (right). As it can be observed, the axilla is 
+		properly recognized.}
+	\label{fig:axilla-recognition}
+\end{figure}
 
@@
 two 
-disconnected curves will appear. This is not necessarily a problem, because a 
-set of disconnected curves has non-zero length (rf?).
+disconnected curves will appear. This is not a problem, because a 
+set of disconnected curves is, in our case, a collection of segments with 
+non-zero length.
 

### 2019-10-01 PaperRMFI2019/samplepaper.tex
small fixes

@@
 %
-\authorrunning{Gonzalez and Mayer}
+\authorrunning{Gonzalez-Tejeda and Mayer}
 % First names are abbreviated in the running head.
@@
 	regions. We show male (left) and female (right) subjects in frontal and 
-	lateral view.}
-	\label{fig:axilla-recognition}
+	lateral view. Note how the regions are correctly segmented for different 
+	gender and body shapes.}
+	\label{fig:mesh_segmented}
 \end{figure}
@@
 
+Figure \ref{fig:mesh_segmented} shows the result of applying these equations on 
+two meshes. Note how the regions are correctly segmented for different gender 
+and body shapes. For example, the male subject on the left is smaller than the 
+female subject on the right. Additionally, the subjects have very different 
+muscular and fat build.
+
 \subsubsection{Axilla recognition}\label{subsec:armpit_recog}
@@
 armpit, also known as axilla. This raises the question whether we can recognize 
-the axilla. What we want is a point in the mesh at the proper location under 
-the arms. One point suffices because we require only a reference along the 
+the axilla. What we want is a point $p_a$ in the mesh at the proper location 
+under 
+the arms. One point suffices because we require only a reference $p^y_a$ along 
+the 
 y-axis to define the chest region according to equation \ref{eq:cr}. Therefore, 
@@
 
-Here $v^x_{min}, v^y_{min}, v^z_{min}$ are vertex with minimum $x$,$y$ and $z$ 
-coordinates, respectively. Distance $d(v^z_{max},v^z_{min})$ is the euclidean 
-distance between vertices with maximum and minimum $z$ coordinate (figure x).
+Here $v^x_{min}, v^y_{min}, v^z_{min}$ are vertex minimum $x$,$y$ and $z$ 
+coordinates, respectively; analog is $v^z_{max}$ the maximum vertex $z$ 
+coordinate. The ray 
+$\iota$ is then determined by points $j_{ls}$ (inside the mesh) and $p_b$ 
+(outside the mesh). Therefore, the ray $\iota$ intersects the mesh at one point 
+$p_a$ (Figure \ref{fig:axilla-recognition}), which we consider the axilla 
+center.
 
@@
 	\caption{Axilla recognition based on the skeleton joint. We cast a ray from 
-	the left shoulder joint in direction to the middle left 
+	the left shoulder joint $j_{ls}$ in direction to the middle left 
 		inferior edge of the bounding box (left). The ray intersects the mesh 
@@
 \subsection{Human Body Mesh Signature}\label{subsec:hbm_signature}
-Intuitively, we would like to measure the chest circumference bellow the arms 
+Intuitively, we would like to measure the chest circumference below the arms 
 at the \textit{widest} part of the torso and the waist circumference at the 
-\textit{narrowest} part after the chest but above the hips. This intuition is 
+\textit{narrowest} part beneath the chest but above the hips. This intuition is 
 compliant 
@@
 standard EN 13402-1 \cite{en13402-1}. Similarly, the pelvis 
-circumference is measured often around the widest part of hips and 
-buttocks. We 
+circumference is measured often around the \textit{widest} part of hips and 
+buttocks. The general idea is to cast the chest, waist and pelvis circumference 
+estimation problem as an optimization problem. If we are able to establish a 
+function that measures geodesics on the mesh, we can search for its maximum, 
+e.g., chest in the chest region.
+
+We 
 can formalize this intuition by considering the cross-sectional length of the 
@@
 use a plane $\boldsymbol{\pi_j}$ parallel (with normal $\vec{n}_{||}$) to the 
-floor to intersect the mesh at a point $q \in 
+floor to intersect the mesh at point $q_j = (0, q^y_j, 0), \,  q^y_j \in 
 \mathbb{R}$ along the y-axis. Since $\mathcal{M}$ is triangulated, the boundary 
@@
 determine the intersection boundary length as
-\begin{equation}
+\begin{equation}\label{eq:boundary_length}
 \mathcal{BL}(\mathcal{M}, \vec{n}_{||}, q) = \sum_{i = 
@@
 
-\begin{figure}[t]
+\begin{figure}[h!]
+	\begin{center}
+		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+		\includegraphics[width=0.5\linewidth]{subject_2_with_cutting_planes_xrays.png}
+	\end{center}
+	\caption{3D mesh iterative slicing. We 
+		can use a plane $\boldsymbol{\pi_j}$ parallel (with normal 
+		$\vec{n}_{||}$) to the 
+		floor to intersect the mesh at point $q_j = (0, q^y_j, 0), \,  q^y_j 
+		\in 
+		\mathbb{R}$ along the y-axis. By varying point $q_j$ (we show here 40), 
+		we can obtain 
+		slices.}
+	\label{fig:subjects_planes_xrays}
+\end{figure}
+
+Starting 
+from the 
+top $q_t$ of the bounding box we slice iteratively mesh $\mathcal{M}$ with 
+plane 
+$\boldsymbol{\pi_j}$ every $m$-meters along the y-axis until we reach the 
+bounding box bottom 
+$q_b$. Figure \ref{fig:subjects_planes_xrays} shows 40 of these 
+slides. Next, we assemble the mesh sliding vector $\vec{\mathcal{L}}$. The 
+elements of 
+this vector are slice point y-coordinates
+
+\begin{align}\label{eq:mesh_slice_vector}
+\vec{\mathcal{L}}(\mathcal{M}, \vec{n}_{||}, m) = \left[ q_t, q_t+m, \cdots, 
+q_b \right]
+\end{align}
+
+Finally, we apply equation \ref{eq:boundary_length} to every element of 
+$\mathcal{L}$ in equation \ref{eq:mesh_slice_vector}. In other words, for every 
+slice at point 
+$q_j$, we compute $\mathcal{BL}(q_j)$. Here we drop from the notation mesh 
+$\mathcal{M}$ and plane normal $\vec{n}_{||}$ because they remain constant. We 
+then can 
+define the \textbf{human body mesh signature} $\mathcal{MS}: 
+\vec{\mathcal{L}} \to \mathbb{R}$ that maps every slice at point $q_j$ to the 
+corresponding boundary length $\mathcal{BL}(q_j)$.
+
+\begin{align}\label{eq:mesh_signature_short}
+\mathcal{MS}(\vec{\mathcal{L}}) = [\mathcal{BL}(\mathcal{L}_1), 
+\mathcal{BL}(\mathcal{L}_2), \cdots, 
+\mathcal{BL}(\mathcal{L}_{|\vec{\mathcal{L}}|})]
+\end{align}
+
+\begin{align}\label{eq:mesh_signature}
+\mathcal{MS}(\mathcal{M}, \vec{n}_{||}, m) = 
+[\mathcal{BL}(q_t), \mathcal{BL}(q_t+m), \cdots, \mathcal{BL}(q_b)]
+\end{align}
+
+\begin{figure}[H]
 	\begin{center}
@@
 
-Next, we assemble the mesh slide length vector $\vec{\mathcal{L}}$. Starting 
-from the 
-top $q_t$ of the bounding box we slice iteratively mesh $\mathcal{M}$ with 
-plane 
-$\boldsymbol{\pi_j}$ every $m$-meters until we reach the bounding box bottom 
-$q_b$. Because the mesh $\mathcal{M}$ and the plane normal $\vec{n}_{||}$ 
-remains the same we can drop them from the notation. For every slice at point 
-$q$, we compute $\mathcal{BL}(q)$.
-
-\begin{align}
-\vec{\mathcal{L}}(\mathcal{M}, \vec{n}_{||}, m) = \left[ \mathcal{BL}(q_t), 
-\mathcal{BL}(q_t+m), \cdots, \mathcal{BL}(q_b) \right]
-\end{align}
-
-Finally, we can define the human body \textbf{mesh signature} $\mathcal{MS}: 
-\mathbb{Z}^+ \to \mathbb{R}$ that maps every slice index $k \in \{0, 1, \cdots, 
-|\mathcal{L}|-1\}$ to the corresponding boundary length $\mathcal{BL}(q)$ in 
-the mesh slide vector $\vec{\mathcal{L}}$.
-
-\begin{align}\label{eq:mesh_signature}
-\mathcal{MS}(k) = \mathcal{BL}(q)
-\end{align}
-
 Figure \ref{fig:hbm_signature} shows the $\mathcal{MS}$ of two meshes (male 
 and female) for 
-$m=0,001$ and plane $\boldsymbol{\pi}$ parallel to the floor (with normal $(0, 
+$m=0,001$ and plane parallel to the floor (with normal 
+$\vec{n}_{||} = (0, 
 1,0)$) using the library trimesh \cite{trimesh}. Note that the function as 
@@
 In general, we expect these \textit{extrema} to be adequate features to 
-calculate the human dimensions. However, there is no consensus in the 
-literature regarding the method to calculate chest, waist and hip 
-circumference. While Yansel et al., 2020 define waist circumference as the 
-blalal. That is why we first establish the regions and the search for local 
-extrema in these regions.
-
-More specifically, we assume that:
+calculate the human dimensions. More specifically, we assume that:
 \begin{enumerate}
-	\item The global maximum $M_g$ represents the length of the largest path 
-	around the arms. From a topographic point of view $M_g$ is the highest peak 
-	of $\mathcal{MS}$. A horizontal line at height proportion $h$ of the peak 
-	intersects 
-	it at two points left $p_l$ and right $p_r$.
-	\item The plane $\boldsymbol{\pi}$ intersects the mesh $\mathcal{M}$ at the 
-	point where the left hip is located defining a path. The length of this 
-	path is $P_{lh}$.	
-	\item The local maximum $M_{pc}$ with largest value other than $M_g$ 
-	immediately prior to $P_{lh}$ represents the pelvis circumference.	
-	\item The local minimum $M_{wc}$ posterior to $p_r$ but prior to $M_{pc}$ 
-	represents waist circumference.
-	\item The local maximum $M_{cc}$ posterior to $p_r$ but prior to $M_{wc}$ 
-	represents 
-	chest circumference. If this local maximum does not exist we set $M_{cc}$ 
-	to the value of the path $\mathcal{BL}(j_{cc})$ with largest value in the 
-	interval $(p_l; M_{wc})$.
+	\item The chest circumference $cc$ is the local maximum within the chest 
+	region.
+	\item The waist circumference $wc$ (not to be confused with the natural 
+	waist line) is the minimum within the waist region.	
+	\item The pelvis circumference $pc$ is the maximum within the pelvis region.
 \end{enumerate}
 
-\subsection{Recognition by interval search}\label{subsec:interval_search}
+\begin{align}\label{eq:cc}
+cc &= \mathcal{L}_i \in \mathcal{CR}\\
+\mathcal{MS}(\mathcal{M}, \vec{n}_{||}, m) &= \mathcal{L}_i \in \mathcal{CR}
+\end{align}
 

### 2019-10-08 PaperRMFI2019/samplepaper.tex
minor fixes

@@
 
+In general, previous work has concentrated on human body shapes not deviating 
+much from the mean. In contrast, we move beyond by exploring 3D meshes 
+reflecting human figures characteristics such as bulky, slim, small and 
+tall subjects.
+
 \subsection{Human Shape Estimation with Artificial Neural Networks}
@@
 y-axis to define the chest region according to equation \ref{eq:cr}. Therefore, 
-we focus on the left shoulder joint $j_{ls} \in \mathbf{J}$. Since the axilla 
+we focus on the right shoulder joint $j_{rs} \in \mathbf{J}$. Since the axilla 
 is related to 
@@
 \begin{align}
-p_b = \bigg(v^x_{min}, v^y_{min}, v^z_{min} + 
+p_c = \bigg(v^x_{min}, v^y_{min}, v^z_{min} + 
 \frac{v^z_{max} - v^z_{min}}{2}\bigg).
@@
 coordinate. The ray 
-$\iota$ is then determined by points $j_{ls}$ (inside the mesh) and $p_b$ 
+$\iota$ is then determined by points $j_{rs}$ (inside the mesh) and $p_b$ 
 (outside the mesh). Therefore, the ray $\iota$ intersects the mesh at one point 
-$p_a$ (Figure \ref{fig:axilla-recognition}), which we consider the axilla 
-center.
+$p_c$ (Figure \ref{fig:axilla-recognition}), which we consider the axilla 
+center. Furthermore, we can consider an strategy to increase the method 
+robustness against the large variability of the human body. Since our method 
+relies on one point to establish the chest upper bound, we identify the 10 
+nearest neighbors in the set of vertices $\mathcal{V}$ to $p_c$ and define 
+$p_a$ to be the 
+vertex with the smallest 
+y coordinate of the neighbors.
 
@@
 elements of 
-this vector are slice point y-coordinates
+this vector are slice points
 
@@
 
-\begin{figure}[h!]
-	\begin{center}
-		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-		\includegraphics[width=\linewidth]{Figure_1.eps}
-	\end{center}
-	\caption{Human Body Mesh Signature for male and female meshes. The 
-		function resembles a rotated silhouette of the human body and exhibits 
-		several \textit{extrema}. See section 
-		\ref{subsec:mesh_signature_extrema} for discussion of these extrema.}
-	\label{fig:qualitative_eval}
-\end{figure}
-
-\subsection{Learning convergence evaluation}\label{subsec:learn_conv}
+\subsection{Calvis-Net and Learning Convergence 
+Evaluation}\label{subsec:learn_conv}
 This experiment demonstrates the plausibility of using calvis to obtain data 
@@
 
-Figure \ref{fig:calvis_net} shows the our prototypical ANN calvis net where the 
-input is a synthetic image from a 3D mesh and the output are the three body 
+Figure \ref{fig:calvis_net} shows our prototypical CNN Calvis-Net where the 
+input is a synthetic image from a 3D mesh and the output are three body 
 dimensions.
 
-Figure \ref{fig:learn_conv} shows that after epoch number 5 the estimation 
+Figure \ref{fig:learning_curve} shows that after epoch number 5 the estimation 
 error decreases and the learning converges.
-
 \begin{figure}[H]
@@
 		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-		\includegraphics[width=\linewidth]{Figure_1.eps}
+		\includegraphics[width=\linewidth]{Calvis-Net.png}
 	\end{center}
-	\caption{Human Body Mesh Signature for male and female meshes. The 
-		function resembles a rotated silhouette of the human body and exhibits 
-		several \textit{extrema}. See section 
-		\ref{subsec:mesh_signature_extrema} for discussion of these extrema.}
-	\label{fig:qualitative_eval}
+	\caption{Calvis-Net.}
+	\label{fig:calvis_net}
 \end{figure}
@@
 		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-		\includegraphics[width=\linewidth]{Figure_1.eps}
+		\includegraphics[width=\linewidth]{Training_val_loss.png}
 	\end{center}
-	\caption{Human Body Mesh Signature for male and female meshes. The 
-		function resembles a rotated silhouette of the human body and exhibits 
-		several \textit{extrema}. See section 
-		\ref{subsec:mesh_signature_extrema} for discussion of these extrema.}
-	\label{fig:qualitative_eval}
+	\caption{Learning convergence evaluation.}
+	\label{fig:learning_curve}
 \end{figure}
@@
 
-The method can be optimized. Further research must be conducted.
+The method operates optimally.
 %

### 2019-10-27 PaperRMFI2019/samplepaper.tex
add pictures

@@
 %
-\title{CALVIS: Chest, wAist and peLVIS circumference from 3D human body meshes	
+\title{CALVIS: chest, waist and pelvis circumference from 3D human body meshes	
 as ground truth for deep learning}
@@
 \begin{abstract}
-In this paper we present CALVIS, a method to calculate chest, waist and 
-pelvis circumference from 3D human body meshes. Our motivation is to use 
-this data as ground truth for learning with convolutional neural networks 
+In this paper we present CALVIS, a method to calculate \textbf{C}hest, 
+w\textbf{A}ist and pe\textbf{LVIS} circumference from 3D human body meshes. Our 
+motivation is to use 
+this data as ground truth for training convolutional neural networks 
 (CNN). Previous work had used the large scale CAESAR dataset or determined 
-$\textit{manually}$ these anthropometrical measurements directly from a person 
+these anthropometrical measurements $\textit{manually}$ from a person 
 or human 3D body meshes. 
 Unfortunately, acquiring these data is a cost and 
-time consuming endeavor. In contrast our method can be used on 
-3D meshes automatically. We conduct two experiments. 
-In the first experiment we synthesize 10 human body meshes. Then we apply 
+time consuming endeavor. In contrast, our method can be used on 
+3D meshes automatically. We synthesize eight human body meshes and 
+apply 
 CALVIS to calculate chest, waist and pelvis circumference. We evaluate the 
-results qualitatively. We observe that the measurements can indeed be used 
-to estimate the shape of a person. The second experiment asses the 
-plausibility of our approach where we use the calculated human dimensions as 
-a ground truth to train a small CNN. After 
+results qualitatively and observe that the measurements can indeed be used 
+to estimate the shape of a person. We then asses the 
+plausibility of our approach by exploiting the calculated human dimensions as 
+ground truth to train a small CNN. After
 having trained the network with 
-our data, we demonstrate that learning converges, achieving $x$ percent 
-prediction error.
+our data, we achieve competitive prediction error.
 Furthermore, we make the implementation of CALVIS publicly available to 
@@
 pelvis circumference having only an image of a person is a challenging problem 
-and involve recognizing the corresponding location of these dimension in the 
+and involve recognizing the corresponding location of these dimensions in the 
 body and estimating their circumference. Additionally, the setting is an  
@@
 %------------------------------------------------------------------------
-\section{Approach}\label{sec:approach}
+\section{Chest, Waist and Pelvis Measurements}\label{sec:approach}
 While human body 
@@
 surface mesh $\mathcal{M}$ that mimics the skin and a corresponding skeleton 
-$\mathbf{J}$. The mesh $\mathcal{M} \in \mathbb{R}^{3N}$, which is a boundary 
+$\mathbf{J}$. The mesh $\mathcal{M}$, which is a boundary 
 representation stores 
@@
 rest joint locations from vertices in the rest 
-pose. A new mesh $\mathcal{M}_{new}$ can be then generated
+pose. A new mesh $\mathcal{M}_{new}$ can be then generated using the SMPL model 
+$M$
 
@@
 parallel to the 
-ground at shoulder height at a $90^\circ$ angle (SMPL normalized pose
+ground at shoulder height at a $90^\circ$ angle (SMPL zero pose
 $\vec{\theta}^*$). Additionally, we assume that the mesh 
@@
 right-to-left, inferior-to-superior and posterior-to-anterior, respectively. If 
-the mesh has another orientation we can always apply transformations to 
+the mesh has another orientation we can always apply rigid transformations to 
 LSA-align it.
@@
 
-We observe that the chest circumference is usually measure bellow the armpits, 
+We observe that the chest circumference is usually measure below the armpits, 
 also known as axilla, but above the natural waist. Similarly, the pelvis 
@@
 $j_{nw}$, $j_{pl}$, 
-$j_{lh} \in \mathbf{J}$ be the natural waist, pelvis and left hip joints, 
-respectively.
+$j_{rh} \in \mathbf{J}$ be the natural waist, pelvis and right hip joints 
+(joints with identifier $\mathtt{Spine1}$, $\mathtt{Pelvis}$, $\mathtt{R\_Hip}$ 
+in 
+$\mathbf{J}$), respectively.
 
@@
 \begin{align}\label{eq:pr}
-\mathcal{PR} = \big(v^y_i \, | \, j^y_{pl} > v^y_i \geq j^y_{lh}\big)
+\mathcal{PR} = \big(v^y_i \, | \, j^y_{pl} > v^y_i \geq j^y_{rh}\big)
 \end{align}
@@
 As mentioned above, we would like to measure the chest circumference below the 
-armpit, also known as axilla. This raises the question whether we can recognize 
+armpit, also known as axilla. This raises the question how we can recognize 
 the axilla. What we want is a point $p_a$ in the mesh at the proper location 
@@
 
+\begin{figure}[t]
+	\begin{center}
+		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+		\includegraphics[width=\linewidth]{axilla_recognition_final.png}
+	\end{center}
+	\caption{Axilla recognition based on the skeleton joint. We cast a ray from 
+		the left shoulder joint $j_{ls}$ in direction to the middle left 
+		inferior edge of the bounding box (left). The ray intersects the mesh 
+		at point $p_c$ (red) that we consider the axilla center. We plot the 10 
+		nearest vertices to $p_c$ (right). Point $p_a$ is the nearest vertex 
+		with smallest y coordinate. As it can be observed, the axilla is 
+		properly recognized.}
+	\label{fig:axilla-recognition}
+\end{figure}
+
 \begin{align}
 p_c = \bigg(v^x_{min}, v^y_{min}, v^z_{min} + 
-\frac{v^z_{max} - v^z_{min}}{2}\bigg).
+\frac{|v^z_{max} - v^z_{min}|}{2}\bigg).
 \end{align}
@@
 center. Furthermore, we can consider an strategy to increase the method 
-robustness against the large variability of the human body. Since our method 
+robustness against the large variability of the human body. Since this approach 
 relies on one point to establish the chest upper bound, we identify the 10 
 nearest neighbors in the set of vertices $\mathcal{V}$ to $p_c$ and define 
-$p_a$ to be the 
-vertex with the smallest 
-y coordinate of the neighbors.
+$p_a$ to be the vertex with the smallest y coordinate of the neighbors.
 
@@
 geodesic on the mesh. Next subsection discuss how.
-
-\begin{figure}[H]
-	\begin{center}
-		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-		\includegraphics[width=\linewidth]{axilla_recognition_final.png}
-	\end{center}
-	\caption{Axilla recognition based on the skeleton joint. We cast a ray from 
-	the left shoulder joint $j_{ls}$ in direction to the middle left 
-		inferior edge of the bounding box (left). The ray intersects the mesh 
-		at point $p_a$ that we consider the axilla center. We plot the 10 
-		nearest vertices to $p_a$ (right). As it can be observed, the axilla is 
-		properly recognized.}
-	\label{fig:axilla-recognition}
-\end{figure}
 
@@
 buttocks. The general idea is to cast the chest, waist and pelvis circumference 
-estimation problem as an optimization problem. If we are able to establish a 
-function that measures geodesics on the mesh, we can search for its maximum, 
+estimation problem as a constrained optimization problem. If we are able to 
+establish a 
+function that measures meaningful geodesics on the mesh, we can search for its 
+maximum, 
 e.g., chest in the chest region.
 
-We 
-can formalize this intuition by considering the cross-sectional length of the 
-2D intersection curves\cite{book.compu.topo} along the y-axis. Moreover, we 
-can 
-use a plane $\boldsymbol{\pi_j}$ parallel (with normal $\vec{n}_{||}$) to the 
-floor to intersect the mesh at point $q_j = (0, q^y_j, 0), \,  q^y_j \in 
-\mathbb{R}$ along the y-axis. Since $\mathcal{M}$ is triangulated, the boundary 
-of this 
-intersection is a collection of segments $s_i$. Therefore, we can 
-determine the intersection boundary length as
-\begin{equation}\label{eq:boundary_length}
-\mathcal{BL}(\mathcal{M}, \vec{n}_{||}, q) = \sum_{i = 
-	1}^{i = N}s_i
-\end{equation}
-
-Note that for cross sections where $\boldsymbol{\pi_j}$ intersects the legs, 
-two 
-disconnected curves will appear. This is not a problem, because a 
-set of disconnected curves is, in our case, a collection of segments with 
-non-zero length.
-
-\begin{figure}[h!]
+\begin{figure}[H]
 	\begin{center}
@@
 
+We 
+can formalize this intuition by considering the cross-sectional length of the 
+2D intersection curves\cite{yansel} along the y-axis. Moreover, we 
+can 
+use a plane $\boldsymbol{\pi_j}$ parallel (with normal $\vec{n}_{||}$) to the 
+floor to intersect the mesh at point $q_j = (0, q^y_j, 0), \,  q^y_j \in 
+\mathbb{R}$ along the y-axis. Since $\mathcal{M}$ is triangulated, the boundary 
+of this 
+intersection is a polygonal curve consisting in segments with length $s_i$. 
+Therefore, we 
+can 
+determine the intersection boundary length as
+\begin{equation}\label{eq:boundary_length}
+\mathcal{BL}(\mathcal{M}, \vec{n}_{||}, q) = \sum_{i = 
+	1}^{i = N}s_i
+\end{equation}
+
+Note that for cross sections where $\boldsymbol{\pi_j}$ intersects the legs, 
+two 
+disconnected curves will appear. This is not a problem, because a 
+set of disconnected curves is, in our case, a collection of segments with 
+non-zero length.
+
 Starting 
@@
 $q_b$. Figure \ref{fig:subjects_planes_xrays} shows 40 of these 
-slides. Next, we assemble the mesh sliding vector $\vec{\mathcal{L}}$. The 
+slices. Next, we assemble the mesh slicing vector $\vec{\mathcal{L}}$. The 
 elements of 
@@
 \begin{align}\label{eq:mesh_slice_vector}
-\vec{\mathcal{L}}(\mathcal{M}, \vec{n}_{||}, m) = \left[ q_t, q_t+m, \cdots, 
+\vec{\mathcal{L}}(\mathcal{M}, \vec{n}_{||}, m) = \left[ q_t, q_t-m, q_t-2 
+m,\cdots, 
 q_b \right]
@@
 
-Finally, we apply equation \ref{eq:boundary_length} to every element of 
+Finally, we apply equation \ref{eq:boundary_length} to every slice defined in
 $\mathcal{L}$ in equation \ref{eq:mesh_slice_vector}. In other words, for every 
 slice at point 
-$q_j$, we compute $\mathcal{BL}(q_j)$. Here we drop from the notation mesh 
+$q_j$, we compute intersection boundary length $\mathcal{BL}(q_j)$. Here we 
+drop from the notation mesh 
 $\mathcal{M}$ and plane normal $\vec{n}_{||}$ because they remain constant. We 
@@
 \mathcal{MS}(\mathcal{M}, \vec{n}_{||}, m) = 
-[\mathcal{BL}(q_t), \mathcal{BL}(q_t+m), \cdots, \mathcal{BL}(q_b)]
+[\mathcal{BL}(q_t), \mathcal{BL}(q_t-m), \cdots, \mathcal{BL}(q_b)]
 \end{align}
 
-\begin{figure}[H]
+\begin{figure}[t]
 	\begin{center}
@@
 	\item The waist circumference $wc$ (not to be confused with the natural 
-	waist line) is the minimum within the waist region.	
+	waist line based on the joint, see subsection \ref{subsec:three_regions}) 
+	is the minimum within the waist region.	
 	\item The pelvis circumference $pc$ is the maximum within the pelvis region.
@@
 \begin{align}\label{eq:cc}
-cc &= \mathcal{L}_i \in \mathcal{CR}\\
-\mathcal{MS}(\mathcal{M}, \vec{n}_{||}, m) &= \mathcal{L}_i \in \mathcal{CR}
+cc = \underset{\mathcal{BL}(q_j)}{\text{arg max}}\ \mathcal{MS} \quad 
+\text{subject 
+to} \quad p^y_a > q_j \geq j^y_{nw}
+\end{align}
+
+\begin{align}\label{eq:wc}
+wc = \underset{\mathcal{BL}(q_j)}{\text{arg min}}\ \mathcal{MS} \quad 
+\text{subject 
+	to} \quad j^y_{nw} > v^y_i \geq j^y_{pl}
+\end{align}
+
+\begin{align}\label{eq:pc}
+pc = \underset{\mathcal{BL}(q_j)}{\text{arg max}}\ \mathcal{MS} \quad 
+\text{subject 
+	to} \quad j^y_{pl} > v^y_i \geq j^y_{rh}
 \end{align}
@@
 \subsection{Qualitative evaluation}\label{subsec:qualitative_eval}
-Here we evaluate our method qualitatively with method one and method two.
+Here we evaluate our method qualitatively.
 \begin{figure}[H]
@@
 		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-		\includegraphics[width=\linewidth]{subject_6_with_cutting_planes_on_joints.eps}
+		\includegraphics[width=\linewidth]{experiment_1_results.png}
 	\end{center}
-	\caption{Qualitative evaluation for male and female meshes. We evaluate our 
-	method with method one and method two.}
+	\caption{Qualitative evaluation for male and female meshes.}
 	\label{fig:qualitative_eval}
@@
 
-Figure \ref{fig:qualitative_eval} shows the $\mathcal{MS}$ of two meshes (male 
-and female) for 
-$m=0,001$ and plane $\boldsymbol{\pi}$ parallel to the floor (with normal $(0, 
-1,0)$) using the library trimesh \cite{trimesh}. Note that the function as 
-defined by equation \ref{eq:mesh_signature} is bounded and not continuous. It 
-resembles a rotated silhouette of the human body and exhibits several 
-\textit{extrema}.
+Figure \ref{fig:qualitative_eval} shows the calculated dimensions on eight 
+subjects, male subjects no. 1-4 and female subjects no. 5-8. The black paths 
+represent chest, waist and pelvis circumference (from 
+top to bottom) as defined by equations \ref{eq:cc}-\ref{eq:pc}, respectively. 
+We slightly rotate the meshes and add transparency for visualization purposes. 
+Note that our method is able to estimate automatically the human body 
+dimensions for all 
+subjects. One particularity can be observed regarding the chest circumference: 
+while for all male and female subjects except for subject no. 7 the chest 
+circumference is 
+estimated above the breast, for subject no.7 the chest circumference is 
+estimated around the breast.
 
-\subsection{Calvis-Net and Learning Convergence 
-Evaluation}\label{subsec:learn_conv}
-This experiment demonstrates the plausibility of using calvis to obtain data 
+\subsection{Learning with Calvis-Net}\label{subsec:learning}
+This experiment demonstrates the plausibility of employing calvis to obtain 
+data 
 that can be used as a ground truth for machine learning (in general) and 
-specifically as supervising signal for ANN.
+specifically as supervising signal for CNN.
 
-Figure \ref{fig:calvis_net} shows our prototypical CNN Calvis-Net where the 
-input is a synthetic image from a 3D mesh and the output are three body 
-dimensions.
+\subsubsection{Experimental setup} We annotate the CMU dataset with calvis. The 
+automatic annotation process took approximately $1\,h\, 47\, min$ in an 
+enhanced 
+modern personal computer.
 
-Figure \ref{fig:learning_curve} shows that after epoch number 5 the estimation 
-error decreases and the learning converges.
+\subsubsection{Calvis-CMU Dataset} We synthesize x images of every 
+person using the package Blender. To increase the realism of these images we 
+adopt a yansel lighting model. This makes sense because it resembles the way 
+how a person is standing in a room when she/he goes to the tailor for her/his 
+body dimensions to be taken.
+
+\subsubsection{Synthetic images as input} We synthesize x images of every 
+person using the package Blender. To increase the realism of these images we 
+adopt a yansel lighting model. This makes sense because it resembles the way 
+how a person is standing in a room when she/he goes to the tailor for her/his 
+body dimensions to be taken.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+Figure \ref{fig:calvis_net} shows our prototypical CNN Calvis-Net where the 
+input is a synthetic image from a 3D mesh and the output are three body 
+dimensions.
+
+Figure \ref{fig:learning_curve} shows that after epoch number 5 the estimation 
+error decreases and the learning converges.
+
+We achieve mean absolute validation error of 0.061698 m plus +-.
 

### 2019-10-28 PaperRMFI2019/samplepaper.tex
related work and cnn

@@
 % to display URLs in blue roman font according to Springer's eBook style:
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
 \renewcommand\UrlFont{\color{blue}\rmfamily}
@@
 to estimate the shape of a person. We then asses the 
-plausibility of our approach by exploiting the calculated human dimensions as 
-ground truth to train a small CNN. After
+plausibility of our approach by generating
+ground truth with CALVIS to train a small CNN. After
 having trained the network with 
-our data, we achieve competitive prediction error.
+our data, we achieve competitive validation error.
 Furthermore, we make the implementation of CALVIS publicly available to 
@@
 even health and mortality estimation. Researches had 
-named this 
+named these
 measurements body intuitive controls \cite{Allen.2003}, biometric 
@@
 
-3D human body generative models offers such an alternative. We propose to 
-synthesize 3D human body meshes using the SMPL \cite{Loper.2015} generative 
-model. Once we have 
-the 3D meshes we can compute chest, waist and pelvis circumference. The next 
+3D human body generative models offers such an alternative. In the line of previous work, we start by synthesizing 3D human body meshes using the SMPL \cite{Loper.2015} generative 
+model. Unlike other works, once we have 
+the 3D meshes we compute chest, waist and pelvis circumference. The next 
 step after obtaining the 
@@
 images. Finally, in possession of this ground truth we can 
-input this images to the learning algorithm and perform inference.
+input these images to the learning algorithm and train with the human body dimensions as supervision signal.
 
@@
 3D body meshes. $2)$ A prototype deep learning framework (CNN) with synthetic 
-images of 3D human body meshes as input and the human body dimension obtained 
+images of 3D human body meshes as input and the human body dimensions obtained 
 with CALVIS as supervision signal.
 
-\section{Related Work}\label{sec:rel_work}
+\section{Related Work} \label{sec:related_work}
 
-\subsection{Human Body Data synthesis}
-The \cite{Anguelov.2005} SCAPE model opened wide possibilities in the field  
-because it provided the community with a generative model of the human 
-body. However, if (Problem they address) (which method?)(Results?) (Open 
-Problems).
-After some(which, reference here) attempts on improving (say here either 
-quality or spped), Loper et al., 2018 \cite{Loper.2015} developed a generative 
-human body model.(Problem they address) (which method?)(Results?) (Open 
-Problems).
-Pischchulin et al., 2017 \cite{Pishchulin.2017} synthesize data. (Problem they 
-address) (which method?)(Results?) (Open Problems).
-More recently, Joo et al. \cite{Joo.2018} presents a human model with SMPL as a 
-body model and added hand and face. We do not use that more complex model in 
-this paper, that is future work.
-
-\subsection{Human Body Dimensions from 3D models}
-Allen et al., 2003 \cite{Allen.2003} proposed how to relate what they call body 
-intuitive controls, e.g. height, weight, age and sex with PCAs performed on the 
-space X (replace X!) using a linear mapping. Describe more please! (Problems)- 
-make connection to next related work.  
-Sigal et al., 2008 \cite{Sigal.2008} used a generative model (which method?) to 
-estimate what he calls biometric measurements. (Results?) (Open Problems).
-It is obvious that the problem of estimating the shape and pose of a human 
-having only an image it is an under-constrained  (or inverse) problem. 
-\cite{Guan.2013}  argues that (why) this situation can be alleviated by 
-providing the shape model with the capability of keeping the height constant. 
-This is indeed not the case for the original SCAPE model because the height is 
-a semantical parameter and semantical parameters are “spread” over all bases. 
-The arguments goes like this: SCAPE is a good human shape model. At its core 
-this model relates triangles deformations to semantical parameters. One of the 
-first problem one encounters when trying to model the human shape is the model 
-size: because one needs a lot (~6000) triangles to sculpt a human body, you 
-have the same amount of dimensions. Then one applies dimensionality reduction 
-techniques, in this case PCA, having at the end around 20 components. These 
-components do not describe intuitively (are not expressed explicit in the model 
-) human shape characteristics (e.g., height, chest circumference or waist), 
-nevertheless they are the bases of a vector space containing human shapes. Next 
-\cite{Guan.2013} goes an argue that by “rotating” one (or more) of these bases 
-we can vary the other bases  without being forced to vary the height.
-
-Wuhrer and Shu, 2013 \cite{Wuhrer.2013} proposed a method to 
-create/estimate/generate 3D human shapes from traditional anthropometric 
-measurements. They learned a correlation between the 3D bodies meshes and 1D 
-measurements. Then, when predicting a new shape, they find an initial solution 
-based on the learned correlation (yansel WHICH correlation) and refine this 
-solution by a two-step non linear optimization. They build up on two 
-assumptions, namely, that the initial estimation should be in the plausible 
-space of human shapes and second, that, in order to generalized, the model has 
-to be refined without using this prior knowledge. While the first step use 
-information from the learned shape prior, the second step introduce a 
-smoothness constraint on the objective function. Like this work we use a set of 
-traditional anthropometric measurements, unlike them we calculate 1D 
-measurements from 3D human bodies to use them as ground truth for later 
-inference. Their approach is able to capture variation outside the shape space 
-spanned by the training data, in other words, the approach generalized well.
-At the same time, Boisvert et al., 2013 \cite{Boisvert.2013} estimate human 
-shape from measurements (what is that)(which method?)(Results?) (Open 
-Problems). These two works can not be directly quantitatively compared because 
-they use different set of measurements.
-Moreover, Yang et al., 2014 \cite{Yang.2014} developed a method to map 
-principal component to what they call semantical parameters. These semantical 
-parameter are indeed anthropometric measurements, which justify their naming: 
-in contrast to anthropometric meaningless principal components, their model is 
-capable of manipulating concepts like chest and waist 
-circumference.(Method?)(Results?).   
-Tsoli et al., 2014 \cite{Tsoli.2014} extract what they calls anthropometric or 
-tailored measurements introduced model-based anthropometry (what is that)(which 
-method?)(Results?) (Open Problems).
+%-------------------------------------------------------------------------
+\subsection{Human Dimensions Estimation from Images.}
+Using metrology techniques \cite{ams.2008.BenAbdelkaderY08} and mixture of experts model \cite{Sigal.2008} human body dimensions like height, arm span and even weight had been estimated from images.
+Chest and waist size had been considered as well \cite{Guan.2013}.
+These investigations used human dimensions for validation (ground truth) that were directly recovered from individuals.
+In contrary, we calculate them
+consistently from 3D meshes.
+Another significant research direction studies shape as (non necessarily meaningful) parameters of some model. For example \cite{Bogo:ECCV:2016} claim describing the first method 
+to 
+estimate pose and shape from a single image, while \cite{DBLP:Lassner2017} estimates shape from 91 keypoints using decision 
+forests. Shape is understood as the 
+parameters of the SMPL model but not human dimensions.
 
@@
 
+\subsection{Human Body Data Synthesis.}
+The SCAPE model\cite{Anguelov.2005} opened wide possibilities in the field. It 
+provided the scientific community with a method to build realistic 3D human 
+body meshes of different shapes in different poses. In order to synthesize a 
+human body mesh a template body must be deformed. The model exhibits, however, an important limitation, namely the last 
+step on the pipeline is an expensive optimization problem.
+Other researchers had used variation of the SCAPE model (S-SCAPE \cite{Pishchulin.2017}) to synthesize human bodies but focused on people detection.
+
+After some attempts on improving the human models quality, for example, to make 
+more 
+easily capturing the correlation between body shape and pose 
+\cite{HaslerSSRS09}, or to better understand body dimensions (SPRING model 
+\cite{Yang.2014}), Loper et al., 2015 \cite{Loper.2015} developed the SMPL generative 
+human body model. In this work we synthesize 3D human meshes using this 
+model. We will briefly describe the model in subsection \ref{subsec:smpl_model}.
+
+Our approach to synthesize images from 3D meshes has been strongly influence by the recent publication of the large scale dataset SURREAL \cite{varol17_surreal}. This work uses the SMPL model 
+to generate images 
+from humans with random backgrounds. However, no human body dimensions are computed of estimated.
+
+More recently, a human model with added hands and face had been presented \cite{Joo.2018}. We do not use this more complex model 
+because the human dimensions we estimate do not require that level 
+of detail.
+
+\subsection{Human Body Dimensions from 3D Models.}
+Although extensive research has been carried out on human shape estimation, 
+methods to consistently define shape based on 3D mesh 
+anthropometric measurements have been little explored. Only a handful of researchers 
+have 
+reported calculating 1D body dimensions from 3D triangular meshes to use them as ground truth for training and validation in a variety of inference processes.
+
+Early research performed feature analysis on what they 
+call body intuitive controls, e.g. height, weight, age and gender \cite{Allen.2003}  but they do not 
+calculate them. Instead they use the CAESAR demographic data. Recording human dimensions beyond height like body fat and the more abstract ``muscles" are described by \cite{HaslerSSRS09}.
+
+Pertinent to our investigation is also the inverse problem: generating 3D human 
+shapes from traditional anthropometric measurements \cite{Wuhrer.2013}. Like this work we use a set of 
+anthropometric measurements that we call dimensions, unlike them we calculate 
+1D measurements from 3D human bodies to use them as ground truth for later 
+inference.
+
+Strongly related to our work are methods that calculate waist and 
+chest circumference by slicing the mesh on a fixed plane and compute the convex hull of the contour \cite{Guan.2013} or path length from identified (marked) 
+vertices on the 3D mesh \cite{Boisvert.2013,Dibra.2016a,Dibra.2016b}. However, is not clear how they define the human body dimensions.
+
+In contrast, we do not 
+calculate the dimensions from fix vertices on the template 
+mesh. Instead, we 
+take a more anthropometric approach and use domain knowledge to calculate these 
+measurements.
+
 \subsection{Human Shape Estimation with Artificial Neural Networks}
 A huge amount of research has been conducted in recent years to address the 
-problem of 3D/2D human shape estimation using ANNs. Experimented with different 
-architectures.
-An state-of-the-art method is \cite{kanazawaHMR18} where they estimate human 
-shape and pose.
+problem of 3D/2D human shape estimation using ANNs. A state-of-the-art method 
+is \cite{kanazawaHMR18} where they estimate human 
+shape and pose. While these ANN's output are human body models parameters 
+(i.e., $\beta$s in \cite{Dibra.2016a} and \cite{varol18_bodynet}) our network 
+is 
+capable to output human dimensions directly.
 
@@
 can formalize this intuition by considering the cross-sectional length of the 
-2D intersection curves\cite{yansel} along the y-axis. Moreover, we 
+2D intersection curves along the y-axis. Moreover, we 
 can 
@@
 		function resembles a rotated silhouette of the human body and exhibits 
-		several \textit{extrema}. See section 
-		\ref{subsec:mesh_signature_extrema} for discussion of these extrema.}
+		several \textit{extrema}.}
 	\label{fig:hbm_signature}
@@
 circumference. Since we do not have ground truth, we evaluate the results 
-qualitatively by comparing our method 
-with \cite{Dibra.2016b}.
+qualitatively.
 The second 
@@
 dimensions to an artificial neural network. After having trained the network 
-with our data, we show that learning converges.
+with our data, we show that the network is able to learn the task.
 
@@
 \subsection{Learning with Calvis-Net}\label{subsec:learning}
-This experiment demonstrates the plausibility of employing calvis to obtain 
+This experiment demonstrates the plausibility of employing CALVIS to obtain 
 data 
@@
 
-\subsubsection{Experimental setup} We annotate the CMU dataset with calvis. The 
+\subsubsection{Experimental setup} We annotate the CMU dataset with CALVIS. The 
 automatic annotation process took approximately $1\,h\, 47\, min$ in an 
@@
 \section{Conclusion}
-
-The method operates optimally.
+In this paper we presented CALVIS, a method to calculate chest, waist and pelvis circumference from 3D human meshes. 
+We demonstrate that our approach can be used to train a CNN by imputing synthetic images of humans and using the measurements calculated with CALVIS as supervision signal.
+Furthermore, we contribute with a prototype CNN CALVIS-NET. Our experiments show that the CNN is able to learn how to perform this task, achieving mean absolute validation error of 0.061698 m plus +-.
+The code 
+and data use 
+in this paper will be made publicly available for researchers.
 %

### 2019-10-29 PaperRMFI2019/samplepaper.tex
fix axilla recognition and mesh signature

@@
 A huge amount of research has been conducted in recent years to address the 
-problem of 3D/2D human shape estimation using ANNs. A state-of-the-art method 
+problem of 3D/2D human shape estimation using CNNs. A state-of-the-art method 
 is \cite{kanazawaHMR18} where they estimate human 
-shape and pose. While these ANN's output are human body models parameters 
+shape and pose. While these CNN's output are human body models parameters 
 (i.e., $\beta$s in \cite{Dibra.2016a} and \cite{varol18_bodynet}) our network 
@@
 		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-		\includegraphics[width=\linewidth]{axilla_recognition_final.png}
+		\includegraphics[width=\linewidth]{axilla_recognition_80_NN.png}
 	\end{center}
 	\caption{Axilla recognition based on the skeleton joint. We cast a ray from 
-		the left shoulder joint $j_{ls}$ in direction to the middle left 
+		the right shoulder joint $j_{rs}$ (red point inside the mesh) in direction to the middle left 
 		inferior edge of the bounding box (left). The ray intersects the mesh 
-		at point $p_c$ (red) that we consider the axilla center. We plot the 10 
-		nearest vertices to $p_c$ (right). Point $p_a$ is the nearest vertex 
+		at point $p_c$ (red) that we consider the axilla center. We plot the 80 
+		nearest vertices to $p_c$ (right). Among these vertices point $p_a$ is the vertex 
 		with smallest y coordinate. As it can be observed, the axilla is 
@@
 \begin{align}
-p_c = \bigg(v^x_{min}, v^y_{min}, v^z_{min} + 
+p_b = \bigg(v^x_{min}, v^y_{min}, v^z_{min} + 
 \frac{|v^z_{max} - v^z_{min}|}{2}\bigg).
@@
 robustness against the large variability of the human body. Since this approach 
-relies on one point to establish the chest upper bound, we identify the 10 
+relies on one point to establish the chest upper bound, we identify the 80 
 nearest neighbors in the set of vertices $\mathcal{V}$ to $p_c$ and define 
@@
 
-Note that for cross sections where $\boldsymbol{\pi_j}$ intersects the legs, 
-two 
-disconnected curves will appear. This is not a problem, because a 
-set of disconnected curves is, in our case, a collection of segments with 
-non-zero length.
-
 Starting 
@@
 		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-		\includegraphics[width=\linewidth]{Figure_1.eps}
+		\includegraphics[width=\linewidth]{mesh_signature.png}
 	\end{center}

### 2019-10-30 PaperRMFI2019/Paper_ID_25_Draft.tex
anonym submission

--- 2019-10-29 PaperRMFI2019/samplepaper.tex
@@
 %
-\titlerunning{Chest, wAist and peLVIS circumference from 3D human body meshes}
+\titlerunning{Chest, waist and pelvis circumference from 3D human body meshes}
 % If the paper title is too long for the running head, you can set
@@
 %
-\author{Yansel Gonzalez Tejeda\orcidID{0000-0003-1002-3815} \and
-Helmut Mayer\orcidID{1111-2222-3333-4444}}
+\author{Author1\orcidID{0000-0000-0000-0000} \and
+Author2\orcidID{0000-0000-0000-0000}}
 %
-\authorrunning{Gonzalez-Tejeda and Mayer}
+\authorrunning{Author1 and Author2}
 % First names are abbreviated in the running head.
@@
 %
-\institute{Paris Lodron University of 
-	Salzburg, Kapitelgasse 4-65020 Salzburg, Austria
-\url{https://www.uni-salzburg.at}}
+\institute{Institute1}
 %
@@
 experiment serves to asses the plausibility of our approach to use the 
-synthetic data for deep learning. We input the calculated human 
-dimensions to an artificial neural network. After having trained the network 
-with our data, we show that the network is able to learn the task.
+synthetic data for deep learning.
 
 \subsection{Qualitative evaluation}\label{subsec:qualitative_eval}
-Here we evaluate our method qualitatively.
+A qualitative evaluation is in this case pertinent.
+There is currently no benchmark to measure how accurate the chest, waits and pelvis circumference can be.
+The main issue is to identify \textit{where} these dimensions are located in the body.
+For instance, even domain experts like tailors and anthropometrists can provide human body dimensions with limited precision.
 \begin{figure}[H]
@@
 dimensions for all 
-subjects. One particularity can be observed regarding the chest circumference: 
-while for all male and female subjects except for subject no. 7 the chest 
-circumference is 
-estimated above the breast, for subject no.7 the chest circumference is 
-estimated around the breast.
+subjects. The dimensions are indeed estimated at locations where domain experts regularly identify them.
 
@@
 data 
-that can be used as a ground truth for machine learning (in general) and 
-specifically as supervising signal for CNN.
+that can be used as a ground truth for machine learning (in general) and particularly as supervising signal for CNN.
 
-\subsubsection{Experimental setup} We annotate the CMU dataset with CALVIS. The 
+\subsubsection{Experimental setup.} First, we assemble our Calvis-CMU Dataset.
+We synthesize 3400 grayscale images (1700 of each gender) of human body meshes generated with parameters from the CMU dataset using Blender.
+To increase the realism of these images we
+adopt an indoor lighting model with one light source and white background. This makes sense because it resembles the way 
+how a person is standing in a room when she attends to the tailor for her 
+body dimensions to be taken.
+Subsequently, we annotate the CMU dataset with CALVIS. The 
 automatic annotation process took approximately $1\,h\, 47\, min$ in an 
-enhanced 
-modern personal computer.
-
-\subsubsection{Calvis-CMU Dataset} We synthesize x images of every 
-person using the package Blender. To increase the realism of these images we 
-adopt a yansel lighting model. This makes sense because it resembles the way 
-how a person is standing in a room when she/he goes to the tailor for her/his 
-body dimensions to be taken.
-
-\subsubsection{Synthetic images as input} We synthesize x images of every 
-person using the package Blender. To increase the realism of these images we 
-adopt a yansel lighting model. This makes sense because it resembles the way 
-how a person is standing in a room when she/he goes to the tailor for her/his 
-body dimensions to be taken.
+enhanced modern personal computer.
 
@@
 Figure \ref{fig:calvis_net} shows our prototypical CNN Calvis-Net where the 
-input is a synthetic image from a 3D mesh and the output are three body 
+input is a synthetic image from a 3D human mesh and the output are three body 
 dimensions.
-
-Figure \ref{fig:learning_curve} shows that after epoch number 5 the estimation 
-error decreases and the learning converges.
-
-We achieve mean absolute validation error of 0.061698 m plus +-.
-
-\begin{figure}[H]
-	\begin{center}
-		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-		\includegraphics[width=\linewidth]{Training_val_loss.png}
-	\end{center}
-	\caption{Learning convergence evaluation.}
-	\label{fig:learning_curve}
-\end{figure}
+Implemented with pytorch \cite{paszke2017automatic}.
+We train the network for 20 epochs and perform 3-fold cross-validation  with skorch.
+We achieve mean absolute validation error of 12 mm.
 
@@
 We demonstrate that our approach can be used to train a CNN by imputing synthetic images of humans and using the measurements calculated with CALVIS as supervision signal.
-Furthermore, we contribute with a prototype CNN CALVIS-NET. Our experiments show that the CNN is able to learn how to perform this task, achieving mean absolute validation error of 0.061698 m plus +-.
+Furthermore, we contribute with a prototype CNN CALVIS-NET. Our experiments show that the CNN is able to learn how to perform this task, achieving competitive mean absolute validation error.
 The code 

### 2020-03-04 PaperRMFI2019/Response_to_Reviewers.tex
update

\documentclass{article}
\usepackage{a4wide}
\title{Response to the Reviewer's Comments}
\author{Yansel Gonzalez Tejeda \and	Helmut Mayer}
\begin{document}

\maketitle

We thank the reviewers for identifying the weaknesses in our paper and 
providing us the opportunity to strengthen our research prior to publication.

The comments of the reviewers have been very useful, for they
made us aware that some major points we were trying to convey
remained obscure even to well-informed readers.

Following up
on the reviewers' suggestions, we have restructured the paper
by changing the order of some sections, by putting more emphasis
on motivation, and by adding clarifications at crucial spots.

In addition, we have also corrected all factual errors and
minor infelicities of presentation that the reviewers brought
to our attention. Below we indicate for each individual comment
how we have dealt with it.

\section*{Reviewer 1}
\begin{verbatim}
> 1)English and equations in the current paper are terrible. The authors need
> to improve the spelling, structure and presentation of the paper.
\end{verbatim}

\begin{verbatim}
> 2) The authors used many abbreviation words without providing any explanation.
\end{verbatim}

For all abbreviation we add the corresponding meaning. For example, Skinned 
Multi-Person Linear (SMPL),

\begin{verbatim}
> 3) There are several typo errors.
> For example:
> pg 3 :
> The SCAPE model[3] opened wide possibilities in the field. ??? which field ?
\end{verbatim}

We added the clarification: "in the field of human shape estimation".

\begin{verbatim}
> has been strongly influence --> influenced
> no human body dimensions are computed of estimated.--> from the estimated
> model
> do not require that level of detail. --> such level of detail
\end{verbatim}

 We have corrected these errors.

\begin{verbatim}
> 4) The authors used the SMPL generative human body model, developed in 2015
> to synthesize 3D human meshes.
\end{verbatim}

Yes, we do. Here we are not able to grasp the intention of the 
reviewer.

\begin{verbatim}
> 5) pg 13, it is not accurate to say "The automatic annotation process took
> approximately 1 h 47 min in an enhanced modern personal computer." What are
> the characteristics of the computer ?
\end{verbatim}

\begin{verbatim}
> 6) The description of the bloc diagram of the CNN Calvis-Net depicted in fig
> 6, page 12, is missed; The proposed CNN architecture is not convincing. No
> detail has been provided about the relation and the functioning of the
> weight, the convolutional and the FC layers.
\end{verbatim}

\begin{verbatim}
> 7) The results are far from being convincible. Experimental results are with
> limited 3D articulated meshes. It would be better if some quantified
> indicators are used (Accuracy assessment).
\end{verbatim}

We take the point, and we think our new version is much clearer.

\section*{Reviewer 2}
\begin{verbatim}
> 1). It is not clear how 8 images can be used to train CNN with ground trut
> of 3 measures.
\end{verbatim}
\begin{verbatim}
> 2). It is not clear how novel the proposed measurement calculation is.
\end{verbatim}
\begin{verbatim}
> 3). there is no comparison with existing methods
\end{verbatim}

We read the objection of the reviewer as a complaint about the
story line. Our restructuring should have remedied this.

We now emphasize the real reason why we want the reduction axioms:
as a tool for {\em compositional analysis} of the epistemic effects of
many different types of information-carrying event. It is actually
surprising that this is possible. We see this compositional analysis
as the heart of dynamic epistemic logic, not just a negotiable
'luxury' for some cases. As a side-effect, such axioms
'reduce' a complete dynamic epistemic language to its static
epistemic base -- but this is a consequence of the analysis,
not the main motivation. Of course, as we now also stress, this
reduction does have another interesting interpretation by itself:
the static language must be rich enough to 'pre-encode' the
effects of the relevenat class of informational events. This
is a requirement on optimal language design which is also known
from other areas of logic, such as conditional logic vis-a-vis
belief revision. Finally, and we may have given the wrong
impression that *this* was our main point: the reduction
analysis tends to make for simpler completeness proofs,
and some direct borrowing of known properties of the
static base into the full dynamic system.

What we also find interesting is how this methodology puts us on
the track of new epistemic operators that have not been isolated
as important before, even though they were there just below the
surface. In particular, relativized common knowledge seems a
new notion of independent interest.

\section*{Reviewer 3}
\begin{verbatim}
> Overall, the paper is very well written. However, the main contributions are
> not clear.
\end{verbatim}

\begin{verbatim}
> The segmentation method is also too constrained as it requires the
> shapes to be a pre-defined position.
\end{verbatim}

\begin{verbatim}
> The paper should also try and compare with other existing segmentation
> algorithms. This is a very well studied topic, see for example:
> https://scholar.google.com.au/scholar?
> q=3d+mesh+segmentation&hl=en&as_sdt=0&as_vis=1&oi=scholart
\end{verbatim}

While we appreciate the reviewer recommendation, it has to be said that we do 
not focus on a comparative analysis of segmentation algorithms. Nevertheless, 
we do think that we could perform such as analysis on future works.

\section*{Reviewer 4}
\begin{verbatim}
> Thank you for sharing the generated database.
\end{verbatim}

We are glad to contribute and thank the reviewer for this encouraging, 
motivational and 
constructive comment.

\section*{Reviewer 5}
\begin{verbatim}
> The main contribution of this paper is to computing the human body dimensions
> based on the geometric methods and meanwhile to testing the CNN-based
> regression method. However, I have the following concerns:
> 1. The experimental details related to the CNN-based method are missing. The
> detailed hyper-parameters used for CNN training and testing are missing.
\end{verbatim}

The reviewer is right. We add the experimental details. See also address to 
reviewer 5

\begin{verbatim}
> 2. There is no comparisons with other related methods. The error of 12mm
> achieved in this paper has no reference score.
\end{verbatim}

\begin{verbatim}
> 3. Overall, I think the problem of 3D human shape measurement is a important
> task, and the geometric method used in this paper has a certain contribution
> to this task.
\end{verbatim}

We are glad to contribute and thank the reviewer for this encouraging, 
motivational and 
constructive comment.

\begin{verbatim}
> 4. The presentation of this paper is not smooth.
\end{verbatim}

The new presentation makes our intentions clearer, we think.
The completeness proof of the logic of epistemic action models as
provided by Baltag, Moss and Solecki is complicated. Our method of
reduction axioms allows us to `lift' the elegant PDL completeness
proof to the logic of epistemic action models. And again: the
reduction axioms that we find are interesting in their own right
as we are after compositional analysis of epistemic effects of events
observed in groups of agents, and earlier dynamic epistemic logic were
simply unable to provide that methodology for common knowledge.

The `point' of LCC is to show that `really' epistemic PDL, contrary to
what the designs of intricate logics of communication and knowledge
suggest, is all that is needed for a rich logic of communication and
change. So if anything, this is a new vindication of PDL, rather than
a criticism of it.

It has to be said, though, that we do not provide a knock-down argument
why this full system is {\em needed} for our style of analysis. We have
not been able to find anything weaker that works, but our list of
open questions at the end does ask if other weaker 'solutions' exist.

\section*{Reviewer 7}
\begin{verbatim} 
> Very interesting work with a recent bibliographic study, nevertheless the
> experimentation part lacks comparative study with the existing one and
> especially in term of algorithmic complexity
\end{verbatim}

We hope that our new version is much more focussed.

The author is right on one further point. We have chosen to add
events that change the world to the standard DEL-framework, since
we feel that this increases the scope with little effort, while
still operating with the same methodology. But it is clear that
this is orthogonal to our main points. We have considered taking
it out (but that seemed a pity), or to put it into a separate
section: but that would lead to too much duplication. Our solution
now is to leave the story combined, while pointing out to the reader
who so prefers that a 'change-free' reading of our main notions and
results can be obtained by merely omitting all our technical talk
about substitutions.

\begin{verbatim}
> As far as style is concerned, the work "perspicuous" appears three
> times on the first page; once in the abstract, and twice in the
> second paragraph. While perspicuous is a delicious word, it is rare
> enough that seeing it three times makes one frown.
\end{verbatim}

We have rephrased things using a wider repertoire of adjectives.

\begin{verbatim}
> Also, typo on p.3,
> first paragraph of 2.1: "PLaza" instead of "Plaza".
\end{verbatim}

Corrected.

\begin{verbatim} 
>>REFEREE REPORT 2<<
> List of typos, corrections and comments:
>
> 1. One of the key definitions ...
\end{verbatim}

The referee is correct that this definition was wrong.

The following change solves the problem. We now take the transitive
closure rather than the *reflexive* transitive closure in the
definition. We have adapted the rest of the text including the
axioms accordingly, and now also the remark on page 5 is correct.

\end{document}

### 2020-03-04 PaperRMFI2019/Paper_ID_25_CameraReady.tex
update

--- 2019-10-30 PaperRMFI2019/Paper_ID_25_Draft.tex
@@
 %
-\author{Author1\orcidID{0000-0000-0000-0000} \and
-Author2\orcidID{0000-0000-0000-0000}}
+\author{Yansel Gonzalez-Tejeda\orcidID{0000-0003-1002-3815} \and
+	Helmut Mayer\orcidID{0000-0002-2428-0962}}
 %
-\authorrunning{Author1 and Author2}
+\authorrunning{Gonzalez-Tejeda and Mayer}
 % First names are abbreviated in the running head.
@@
 %
-\institute{Institute1}
+\institute{Paris Lodron University of 
+	Salzburg, Kapitelgasse 4-6, 5020 Salzburg, Austria
+	\url{https://www.uni-salzburg.at}}
 %
@@
 
-In the past decade a noticeably amount of researchers have employed this 
+In the past decade a noticeable number of researchers have employed this 
 dataset to investigate human shape estimation. Because the measurement 
@@
 
-3D human body generative models offers such an alternative. In the line of previous work, we start by synthesizing 3D human body meshes using the SMPL \cite{Loper.2015} generative 
+3D human body generative models offers such an alternative. In the line of 
+previous work, we start by synthesizing 3D human body meshes using the Skinned 
+Multi-Person Linear (SMPL) \cite{Loper.2015} generative 
 model. Unlike other works, once we have 
@@
 \subsection{Human Dimensions Estimation from Images.}
-Using metrology techniques \cite{ams.2008.BenAbdelkaderY08} and mixture of experts model \cite{Sigal.2008} human body dimensions like height, arm span and even weight had been estimated from images.
-Chest and waist size had been considered as well \cite{Guan.2013}.
-These investigations used human dimensions for validation (ground truth) that were directly recovered from individuals.
-In contrary, we calculate them
+Using metrology techniques \cite{ams.2008.BenAbdelkaderY08} and mixture of 
+experts model \cite{Sigal.2008} human body dimensions like height, arm span and 
+even weight had been estimated from images. Chest and waist size had been 
+considered as well \cite{Guan.2013}. These investigations used human dimensions 
+for validation (ground truth) that were directly recovered from individuals. In 
+contrast, we calculate them  
 consistently from 3D meshes.
@@
 \subsection{Human Body Data Synthesis.}
-The SCAPE model\cite{Anguelov.2005} opened wide possibilities in the field. It 
+The Shape Completion and Animation of People (SCAPE) model\cite{Anguelov.2005} 
+opened wide possibilities in the field of 
+human shape estimation. It 
 provided the scientific community with a method to build realistic 3D human 
@@
 easily capturing the correlation between body shape and pose 
-\cite{HaslerSSRS09}, or to better understand body dimensions (SPRING model 
+\cite{HaslerSSRS09}, or to better understand body dimensions (Semantic 
+Parametric Reshaping of Human Body Models - SPRING model 
 \cite{Yang.2014}), Loper et al., 2015 \cite{Loper.2015} developed the SMPL generative 
@@
 
-Our approach to synthesize images from 3D meshes has been strongly influence by the recent publication of the large scale dataset SURREAL \cite{varol17_surreal}. This work uses the SMPL model 
+Our approach to synthesize images from 3D meshes has been influenced 
+by the recent publication of the large scale dataset SURREAL 
+\cite{varol17_surreal}. This work uses the SMPL model 
 to generate images 
-from humans with random backgrounds. However, no human body dimensions are computed of estimated.
+from humans with random backgrounds. However, no human body dimensions are 
+computed or estimated.
 
 More recently, a human model with added hands and face had been presented \cite{Joo.2018}. We do not use this more complex model 
-because the human dimensions we estimate do not require that level 
+because the human dimensions we estimate do not require such level 
 of detail.
@@
 \subsection{SMPL Generative Model of the Human Body}\label{subsec:smpl_model}
-In this work we synthesize 3D human meshes using the SMPL
-model \cite{Loper.2015}. The generative nature of our approach establishes this 
+In this work we synthesize 3D human meshes using the Skinned Multi-Person 
+Linear (SMPL) model \cite{Loper.2015}. The generative nature of our approach 
+establishes this 
 model as starting point (and not the 3D mesh). Nevertheless, our method is 
@@
 Once we have a segmented mesh, we search the dimensions within 
-these regions. The body dimensions we want to calculate are 
-geodesic on the mesh. Next subsection discuss how.
+these regions. Next subsection discuss how to calculate geodesic on the mesh to 
+establish a search strategy.
 
@@
 We slightly rotate the meshes and add transparency for visualization purposes. 
-Note that our method is able to estimate automatically the human body 
+Note that our method is able to calculate automatically the human body 
 dimensions for all 
-subjects. The dimensions are indeed estimated at locations where domain experts regularly identify them.
+subjects. The dimensions are indeed calculated at locations where domain 
+experts regularly identify them.
 
@@
 \subsubsection{Experimental setup.} First, we assemble our Calvis-CMU Dataset. 
-We synthesize 3400 grayscale images (1700 of each gender) of human body meshes generated with parameters from the CMU dataset using Blender.
-To increase the realism of these images we
+Using Blender we render 3400 grayscale images (1700 of each gender) of 
+human body meshes generated with parameters from the CMU dataset. To increase 
+the realism of these images we 
 adopt an indoor lighting model with one light source and white background. This makes sense because it resembles the way 
@@
 
-Figure \ref{fig:calvis_net} shows our prototypical CNN Calvis-Net where the 
-input is a synthetic image from a 3D human mesh and the output are three body 
-dimensions.
-Implemented with pytorch \cite{paszke2017automatic}.
-We train the network for 20 epochs and perform 3-fold cross-validation  with skorch.
-We achieve mean absolute validation error of 12 mm.
+Figure \ref{fig:calvis_net} shows our prototypical CNN Calvis-Net implemented 
+with pytorch \cite{paszke2017automatic}. The 
+input is a synthetic grayscale image from a 3D human mesh of size $\mathtt{200 
+x 200 x 
+1}$. The input layer is followed by a convolutional layer $\mathtt{CL}_1$ with 
+$\mathtt{3}$ 2D-kernels of 
+size $\mathtt{5 x 5}$ and max pooling $\mathtt{MP}$ over a $\mathtt{2 x 2}$ 
+volume. The network continues then with the rectified linear activation function
+(ReLU). The last layer (fully connected $\mathtt{FC}$) regresses directly three 
+body 
+dimensions: chest, waist and pelvis circumference. We train the network for 20 
+epochs and perform 3-fold 
+cross-validation, achieving mean absolute validation error of 12 
+mm.
 

### 2020-03-04 notebook/SMPL_widget.py

@@ -1,0 +1,160 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Mar  3 10:18:17 2020
+
+@author: neoglez
+"""
+import sys
+
+hbm_path = "/home/neoglez/hbm/"
+
+sys.path.append(hbm_path)
+
+import numpy as np
+import pickle
+from OSmpl import KJointPredictor, OSmplTemplate, OSmpl
+from Synthesizer import Synthesizer
+import os
+import json
+import math
+
+cmu_dataset_path = '/home/neoglez/cmu'
+cmu_dataset_meshes_path = '/home/neoglez/cmu/dataset/human_body_meshes/'
+cmu_dataset_meshes_path_length = len(cmu_dataset_meshes_path)
+cmu_dataset_annotation_path = '/home/neoglez/cmu/dataset/annotations/'
+
+SMPL_basicModel_f_lbs_path = "./basicModel_f_lbs_10_207_0_v1.0.0.pkl"
+SMPL_basicModel_m_lbs_path = "./basicmodel_m_lbs_10_207_0_v1.0.0.pkl"
+
+smpl_data_folder = ("/home/neoglez/smpl_data/SURREAL/smpl_data/")
+
+smpl_data_filename = ("smpl_data.npz")
+
+smpl_data = np.load(os.path.join(smpl_data_folder, smpl_data_filename))
+
+maleshapes = smpl_data['maleshapes']
+femaleshapes = smpl_data['femaleshapes']
+
+
+betas = {'female': femaleshapes, 'male': maleshapes}
+
+SMPL_basicModel_f_lbs_path = ("/media/neoglez/Data1/privat/PhD_Uni_Salzburg"
+              "/DATASETS/smpl/models/basicModel_f_lbs_10_207_0_v1.0.0.pkl")
+SMPL_basicModel_m_lbs_path = ("/media/neoglez/Data1/privat/PhD_Uni_Salzburg"
+              "/DATASETS/smpl/models/basicmodel_m_lbs_10_207_0_v1.0.0.pkl")
+
+try:
+    # Load pkl created in python 2.x with python 2.x
+    female_model = pickle.load(open(SMPL_basicModel_f_lbs_path, 'rb'))
+    male_model = pickle.load(open(SMPL_basicModel_m_lbs_path, 'rb'))
+except:
+    # Load pkl created in python 2.x with python 3.x
[…]
